---
title: "Clean_R_analysis"
author: "Jikaël Ntoko"
date: "2024-12-03"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Required package
```{r}
if (!require("vcfR")) {
  install.packages("vcfR")
  library(vcfR)
}
# Generate plots
library(ggplot2)
library(kSamples)  # Required for ad.test
library(VGAM) #L-shaped distribution
library(dplyr)
library(tidyr)


library(hierfstat)
if (!requireNamespace("kSamples", quietly = TRUE)) {
  install.packages("kSamples")
}
library(kSamples)


source("./script/custom_function.R") # Import your R script

seed_value <- 123
set.seed(123)
```

## Import Data for minor and without minor allele sampling
```{r}
#Import VCF and get GT data
data_directory <- "./Data/neutral/"
all_vcf <- list.files(path= data_directory, full.names = TRUE, pattern='\\.vcf$')
vcf_data <- import_vcf(all_vcf)


# Normal Data set
data_numeric_list <- list()
for(replicate in seq_along(vcf_data)){
  print(paste0("Processinge replicate: ", replicate))
  data_num <- data_to_numeric(vcf_data[[replicate]])
  data_numeric_list[[paste0("replicate_",replicate)]] <- data_num
}
gc()
```
#Normally distributed effect size
## Without minor allele sampling

```{r}

loci_counts <- c(1, 10, 100, 1000)
norm_replication <- list()

for (number in 1:10) {
  #set.seed(seed_value + number)  # Ensure unique seed per replication
  qst_result_norm <- list()
  
  for (replicate in seq_along(data_numeric_list)) {
    print(paste0("Processing replicate: ", replicate, " replication: ", number))
    
    # Split replicate into 8 populations
    splited_pop <- split_into_pop(data_numeric_list[[replicate]])
    
    # Initialize Qst results for the replicate
    qst_resutl <- list()
    
    for (loci in loci_counts) {
      # Compute phenotype for the 8 populations
      phenotype <- phenotype_calc_norm(splited_pop, loci)
      qst <- Qst_cal(phenotype)
      qst_resutl[[paste0("N_", loci)]] <- qst
    }
    
    # Store Qst results for the replicate
    qst_result_norm[[paste0("replicate_", replicate)]] <- qst_resutl
  }
  
  # Store Qst results for the replication
  norm_replication[[paste0("replication_", number)]] <- qst_result_norm
}

```
### Data comparison & statistical analysis
```{r}
# Define the output folder and create it if necessary
output_folder <- "./result/norm/wo_maf/within_replication_qqplot"
if (!dir.exists(output_folder)) {
  dir.create(output_folder, recursive = TRUE)  # Create folder if it doesn't exist
}

# Loci comparisons
loci_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Output files for statistical results
ks_test_file <- file.path(output_folder, "ks_test_results.txt")
ad_test_file <- file.path(output_folder, "ad_test_results.txt")
anova_file <- file.path(output_folder, "anova_results.txt")
ttest_file <- file.path(output_folder, "t_test_results.txt")

# Initialize file connections
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA and Tukey HSD Results\n")
cat("===========================\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("================\n\n")
sink()

# Loop over replications
for (replication_name in names(norm_replication)) {
  current_replication <- replication[[replication_name]]  # Extract current replication
  
  # Initialize data for ANOVA and T-tests
  all_loci_values <- list()
  
  # Loop over loci comparisons
  for (comparison in loci_comparisons) {
    loci_x <- comparison[1]
    loci_y <- comparison[2]
    
    # Extract and combine data across all replicates for the loci sets
    combined_data <- do.call(rbind, lapply(names(current_replication), function(replicate_name) {
      replicate_data <- current_replication[[replicate_name]]
      data.frame(
        Replicate = replicate_name,
        x = replicate_data[[loci_x]],
        y = replicate_data[[loci_y]]
      )
    }))
    
    # Store data for ANOVA and T-tests
    all_loci_values[[loci_x]] <- combined_data$x
    all_loci_values[[loci_y]] <- combined_data$y
    
    # Perform KS Test
    ks_test <- ks.test(combined_data$x, combined_data$y)
    sink(ks_test_file, append = TRUE)
    cat("KS Test for", loci_x, "vs", loci_y, "in", replication_name, ":\n")
    print(ks_test)
    cat("\n")
    sink()
    
    # Perform Two-Sample Anderson-Darling Test
    if (length(combined_data$x) > 1 && length(combined_data$y) > 1) {
      ad_test <- kSamples::ad.test(combined_data$x, combined_data$y)
      sink(ad_test_file, append = TRUE)
      cat("AD Test for", loci_x, "vs", loci_y, "in", replication_name, ":\n")
      print(ad_test)
      cat("\n")
      sink()
    } else {
      sink(ad_test_file, append = TRUE)
      cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "in", replication_name, "\n\n")
      sink()
    }
    
    # Generate QQ plot
    x_sorted <- sort(combined_data$x, na.last = TRUE)
    y_sorted <- sort(combined_data$y, na.last = TRUE)
    plot_data <- data.frame(x = x_sorted, y = y_sorted)
    
    plot <- ggplot(data = plot_data, aes(x = y, y = x)) +
      geom_point(color = "blue") +
      geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
      labs(
        title = paste(loci_x, "vs", loci_y, "-", replication_name),
        x = paste(loci_y),
        y = paste(loci_x)
      ) +
      theme_minimal() +
      coord_fixed() +
      scale_x_continuous(limits = c(0.0, 0.1)) +
      scale_y_continuous(limits = c(0.0, 0.1))
    
    file_name <- file.path(output_folder, paste0("QQ_Plot_", loci_x, "_vs_", loci_y, "_", replication_name, ".png"))
    ggsave(filename = file_name, plot = plot, width = 6, height = 4)
  }
  
  # Combine data for ANOVA and T-tests
  loci_groups <- unlist(lapply(names(all_loci_values), function(loci) {
    rep(loci, length(all_loci_values[[loci]]))
  }))
  qst_values <- unlist(all_loci_values)
  data <- data.frame(
    LociGroup = factor(loci_groups, levels = names(all_loci_values)),
    QstValue = qst_values
  )
  
  # Perform ANOVA
  anova_results <- aov(QstValue ~ LociGroup, data = data)
  sink(anova_file, append = TRUE)
  cat("ANOVA Results for", replication_name, ":\n")
  print(summary(anova_results))
  cat("\n")
  
  # Tukey's HSD Post-Hoc Test
  cat("Tukey HSD Results for", replication_name, ":\n")
  tukey_results <- TukeyHSD(anova_results)
  print(tukey_results)
  cat("\n")
  sink()
  
  # Perform T-Test
  t_test_results <- pairwise.t.test(
    data$QstValue,
    data$LociGroup,
    p.adjust.method = "bonferroni"
  )
  sink(ttest_file, append = TRUE)
  cat("T-Test Results for", replication_name, ":\n")
  print(t_test_results)
  cat("\n")
  sink()
}

```
### between replication
```{r}
# Set output directory
output_dir <- "./result/norm/wo_maf/between_replication_qqplot/"
if (!dir.exists(output_dir)) dir.create(output_dir)

# Output files for statistical results
ks_test_file <- file.path(output_dir, "ks_test_results.txt")
ad_test_file <- file.path(output_dir, "ad_test_results.txt")
anova_file <- file.path(output_dir, "anova_results.txt")
ttest_file <- file.path(output_dir, "t_test_results.txt")

# Initialize file connections
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA Results\n")
cat("=============\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("==============\n\n")
sink()


# Assuming `replication` is the nested structure
data <- flatten_replication_data(norm_replication)

# Define loci comparisons
loci_comparisons <- list(
  c("N_1", "N_1"),
  c("N_10", "N_10"),
  c("N_100", "N_100"),
  c("N_1000", "N_1000"),
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Perform statistical comparisons and save results
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Filter data for the two loci
  data_x <- data %>% filter(Loci == loci_x) %>% pull(QstValue)
  data_y <- data %>% filter(Loci == loci_y) %>% pull(QstValue)
  
  # Perform KS Test
  if (length(data_x) > 1 && length(data_y) > 1) {
    ks_test <- ks.test(data_x, data_y)
    sink(ks_test_file, append = TRUE)
    cat("KS Test for", loci_x, "vs", loci_y, ":\n")
    print(ks_test)
    cat("\n")
    sink()
  }
  
  # Perform AD Test using kSamples
if (length(data_x) > 1 && length(data_y) > 1) {
  ad_test <- kSamples::ad.test(data_x, data_y)
  sink(ad_test_file, append = TRUE)
  cat("AD Test for", loci_x, "vs", loci_y, ":\n")
  print(ad_test)
  cat("\n")
  sink()
} else {
  sink(ad_test_file, append = TRUE)
  cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "\n\n")
  sink()
}
}

# Grouped data for ANOVA and T-Test
anova_data <- data %>%
  filter(Loci %in% unlist(loci_comparisons)) %>%
  group_by(Loci) %>%
  summarise(QstValues = list(QstValue), .groups = "drop") %>%
  unnest(cols = c(QstValues))

# Perform ANOVA
anova_results <- aov(QstValue ~ Loci, data = data)
sink(anova_file, append = TRUE)
cat("ANOVA Results:\n")
print(summary(anova_results))
cat("\n")
sink()

# Perform T-Test
t_test_results <- pairwise.t.test(
  data$QstValue,
  data$Loci,
  p.adjust.method = "bonferroni"
)
sink(ttest_file, append = TRUE)
cat("T-Test Results:\n")
print(t_test_results)
cat("\n")
sink()
# Define loci comparisons for QQ plots
qqplot_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Generate QQ plots for specified comparisons
for (comparison in qqplot_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Filter data for the two loci
  data_x <- data %>% filter(Loci == loci_x) %>% pull(QstValue)
  data_y <- data %>% filter(Loci == loci_y) %>% pull(QstValue)
  
  if (length(data_x) > 1 && length(data_y) > 1) {
    # Generate QQ plot
    qqplot_data <- data.frame(
      x = sort(data_x),
      y = sort(data_y)
    )
    
    qq_plot <- ggplot(qqplot_data, aes(x = x, y = y)) +
      geom_point(color = "blue") +
      geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
      labs(
        title = paste("QQ Plot:", loci_x, "vs", loci_y),
        x = paste(loci_x ),
        y = paste(loci_y)
      ) +
      theme_minimal() +
      coord_fixed() +
      scale_x_continuous(limits = c(0.0, 0.1)) +
      scale_y_continuous(limits = c(0.0, 0.1))
    
    # Save the QQ plot
    qqplot_file <- file.path(output_dir, paste0("QQ_Plot_", loci_x, "_vs_", loci_y, ".png"))
    ggsave(qqplot_file, qq_plot, width = 6, height = 6)
  } else {
    cat("Insufficient data for QQ Plot for", loci_x, "vs", loci_y, "\n")
  }
}


```
### Average over the 10 iterations
```{r}
# Define loci comparisons
loci_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Create an output folder
output_folder <- "./result/norm/wo_maf//average_qqplots"
if (!dir.exists(output_folder)) dir.create(output_folder)

# Output files for statistical results
ks_test_file <- file.path(output_folder, "ks_test_results.txt")
ad_test_file <- file.path(output_folder, "ad_test_results.txt")
anova_file <- file.path(output_folder, "anova_results.txt")
ttest_file <- file.path(output_folder, "t_test_results.txt")

# Initialize output files
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA and Tukey HSD Results\n")
cat("===========================\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("================\n\n")
sink()

# Loop over loci comparisons
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Average values over all replications for each replicate
  averaged_data <- do.call(rbind, lapply(names(norm_replication[[1]]), function(replicate_name) {
    # Extract replicate data across all replications
    replicate_values <- do.call(rbind, lapply(names(norm_replication), function(replication_name) {
      norm_replication[[replication_name]][[replicate_name]]
    }))
    
    # Ensure data is numeric
    numeric_values <- as.data.frame(lapply(as.data.frame(replicate_values), as.numeric))
    
    # Compute averages for loci_x and loci_y
    data.frame(
      Replicate = replicate_name,
      x = mean(numeric_values[[loci_x]], na.rm = TRUE),
      y = mean(numeric_values[[loci_y]], na.rm = TRUE)
    )
  }))
  
  # Sort values for quantile-quantile plotting
  x_sorted <- sort(averaged_data$x, na.last = TRUE)
  y_sorted <- sort(averaged_data$y, na.last = TRUE)
  
  # Perform Kolmogorov-Smirnov Test
  ks_test <- ks.test(x_sorted, y_sorted)
  sink(ks_test_file, append = TRUE)
  cat("KS Test for", loci_x, "vs", loci_y, ":\n")
  print(ks_test)
  cat("\n")
  sink()
  
    # Perform Anderson-Darling Test using kSamples
  if (length(x_sorted) > 1 && length(y_sorted) > 1) {
    ad_test <- kSamples::ad.test(x_sorted, y_sorted)
    sink(ad_test_file, append = TRUE)
    cat("AD Test for", loci_x, "vs", loci_y, ":\n")
    print(ad_test)
    cat("\n")
    sink()
  } else {
    sink(ad_test_file, append = TRUE)
    cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "\n\n")
    sink()
  }
  
   # Combine data for ANOVA and t-tests
  combined_data <- data.frame(
    Group = rep(c(loci_x, loci_y), each = length(x_sorted)),
    Value = c(x_sorted, y_sorted)
  )
  
  # Perform ANOVA
  anova_results <- aov(Value ~ Group, data = combined_data)
  sink(anova_file, append = TRUE)
  cat("ANOVA Results for", loci_x, "vs", loci_y, ":\n")
  print(summary(anova_results))
  cat("\n")
  
  # Tukey's HSD Post-Hoc Test
  cat("Tukey HSD Results for", loci_x, "vs", loci_y, ":\n")
  tukey_results <- TukeyHSD(anova_results)
  print(tukey_results)
  cat("\n")
  sink()
  
  # Perform t-test
  t_test_results <- t.test(x_sorted, y_sorted)
  sink(ttest_file, append = TRUE)
  cat("T-Test Results for", loci_x, "vs", loci_y, ":\n")
  print(t_test_results)
  cat("\n")
  sink()
  
  # Create a data frame for plotting
  plot_data <- data.frame(x = x_sorted, y = y_sorted)
  
  # Generate QQ plot
  plot <- ggplot(data = plot_data, aes(x = y, y = x)) +
    geom_point(color = "blue") +
    geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
    labs(
      title = paste("Averaged QQ Plot:", loci_x, "vs", loci_y),
      x = paste("Average Quantiles of", loci_y),
      y = paste("Average Quantiles of", loci_x)
    ) +
    theme_minimal() +
    coord_fixed() +
    scale_x_continuous(limits = c(0.0, 0.06)) +
    scale_y_continuous(limits = c(0.0, 0.06))
  
  # Save the plot
  file_name <- file.path(output_folder, paste0("Averaged_QQ_Plot_", loci_x, "_vs_", loci_y, ".png"))
  ggsave(filename = file_name, plot = plot, width = 6, height = 4)
}

```

## With minor allele sampling
```{r}
# Minor allele sampling dataset
minor_data_list <- list()
for(replicate in seq_along(data_numeric_list)){
  print(paste0("Minor allele sampling  - Processing replicate: ", replicate))
  maf_data <- maf(data_numeric_list[[replicate]])
  
  minor_data_list[[paste0("Replicate_", replicate)]] <- maf_data
}

```

```{r}
loci_counts <- c(1, 10, 100, 1000)
norm_minor_replication <- list()

for (number in 1:10) {
  #set.seed(seed_value + number)  # Ensure unique seed per replication
  qst_result_norm <- list()
  
  for (replicate in seq_along(minor_data_list)) {
    print(paste0("Processing replicate: ", replicate, " replication: ", number))
    
    # Split replicate into 8 populations
    splited_pop <- split_into_pop(minor_data_list[[replicate]])
    
    # Initialize Qst results for the replicate
    qst_resutl <- list()
    
    for (loci in loci_counts) {
      #set.seed(seed_value + number + loci + replicate)  # Unique seed for loci, replicate, and replication
      
      # Compute phenotype for the 8 populations
      phenotype <- phenotype_calc_norm(splited_pop, loci)
      qst <- Qst_cal(phenotype)
      qst_resutl[[paste0("N_", loci)]] <- qst
    }
    
    # Store Qst results for the replicate
    qst_result_norm[[paste0("replicate_", replicate)]] <- qst_resutl
  }
  
  # Store Qst results for the replication
  norm_minor_replication[[paste0("replication_", number)]] <- qst_result_norm
}

```

### within replication
```{r}
# Define the output folder and create it if necessary
output_folder <- "./result/norm/maf/within_replication_qqplot"
if (!dir.exists(output_folder)) {
  dir.create(output_folder, recursive = TRUE)  # Create folder if it doesn't exist
}

# Loci comparisons
loci_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Output files for statistical results
ks_test_file <- file.path(output_folder, "ks_test_results.txt")
ad_test_file <- file.path(output_folder, "ad_test_results.txt")
anova_file <- file.path(output_folder, "anova_results.txt")
ttest_file <- file.path(output_folder, "t_test_results.txt")

# Initialize file connections
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA and Tukey HSD Results\n")
cat("===========================\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("================\n\n")
sink()

# Loop over replications
for (replication_name in names(norm_minor_replication)) {
  current_replication <- norm_minor_replication[[replication_name]]  # Extract current replication
  
  # Initialize data for ANOVA and T-tests
  all_loci_values <- list()
  
  # Loop over loci comparisons
  for (comparison in loci_comparisons) {
    loci_x <- comparison[1]
    loci_y <- comparison[2]
    
    # Extract and combine data across all replicates for the loci sets
    combined_data <- do.call(rbind, lapply(names(current_replication), function(replicate_name) {
      replicate_data <- current_replication[[replicate_name]]
      data.frame(
        Replicate = replicate_name,
        x = replicate_data[[loci_x]],
        y = replicate_data[[loci_y]]
      )
    }))
    
    # Store data for ANOVA and T-tests
    all_loci_values[[loci_x]] <- combined_data$x
    all_loci_values[[loci_y]] <- combined_data$y
    
    # Perform KS Test
    ks_test <- ks.test(combined_data$x, combined_data$y)
    sink(ks_test_file, append = TRUE)
    cat("KS Test for", loci_x, "vs", loci_y, "in", replication_name, ":\n")
    print(ks_test)
    cat("\n")
    sink()
    
      # Perform AD Test using kSamples
  if (length(combined_data$x) > 1 && length(combined_data$y) > 1) {
    ad_test <- kSamples::ad.test(combined_data$x, combined_data$y)
    sink(ad_test_file, append = TRUE)
    cat("AD Test for", loci_x, "vs", loci_y, "in", replication_name, ":\n")
    print(ad_test)
    cat("\n")
    sink()
  } else {
    sink(ad_test_file, append = TRUE)
    cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "in", replication_name, "\n\n")
    sink()
  }
    
    # Generate QQ plot
    x_sorted <- sort(combined_data$x, na.last = TRUE)
    y_sorted <- sort(combined_data$y, na.last = TRUE)
    plot_data <- data.frame(x = x_sorted, y = y_sorted)
    
    plot <- ggplot(data = plot_data, aes(x = y, y = x)) +
      geom_point(color = "blue") +
      geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
      labs(
        title = paste(loci_x, "vs", loci_y, "-", replication_name),
        x = paste(loci_y),
        y = paste(loci_x)
      ) +
      theme_minimal() +
      coord_fixed() +
      scale_x_continuous(limits = c(0.0, 0.1)) +
      scale_y_continuous(limits = c(0.0, 0.1))
    
    file_name <- file.path(output_folder, paste0("QQ_Plot_", loci_x, "_vs_", loci_y, "_", replication_name, ".png"))
    ggsave(filename = file_name, plot = plot, width = 6, height = 4)
  }
  
  # Combine data for ANOVA and T-tests
  loci_groups <- unlist(lapply(names(all_loci_values), function(loci) {
    rep(loci, length(all_loci_values[[loci]]))
  }))
  qst_values <- unlist(all_loci_values)
  data <- data.frame(
    LociGroup = factor(loci_groups, levels = names(all_loci_values)),
    QstValue = qst_values
  )
  
  # Perform ANOVA
  anova_results <- aov(QstValue ~ LociGroup, data = data)
  sink(anova_file, append = TRUE)
  cat("ANOVA Results for", replication_name, ":\n")
  print(summary(anova_results))
  cat("\n")
  
  # Tukey's HSD Post-Hoc Test
  cat("Tukey HSD Results for", replication_name, ":\n")
  tukey_results <- TukeyHSD(anova_results)
  print(tukey_results)
  cat("\n")
  sink()
  
  # Perform T-Test
  t_test_results <- pairwise.t.test(
    data$QstValue,
    data$LociGroup,
    p.adjust.method = "bonferroni"
  )
  sink(ttest_file, append = TRUE)
  cat("T-Test Results for", replication_name, ":\n")
  print(t_test_results)
  cat("\n")
  sink()
}

```
### between replication
```{r}
# Set output directory
output_dir <- "./result/norm/maf/between_replication_qqplot/"
if (!dir.exists(output_dir)) dir.create(output_dir)

# Output files for statistical results
ks_test_file <- file.path(output_dir, "ks_test_results.txt")
ad_test_file <- file.path(output_dir, "ad_test_results.txt")
anova_file <- file.path(output_dir, "anova_results.txt")
ttest_file <- file.path(output_dir, "t_test_results.txt")

# Initialize file connections
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA Results\n")
cat("=============\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("==============\n\n")
sink()


# Assuming `replication` is the nested structure
data <- flatten_replication_data(norm_minor_replication)

# Define loci comparisons
loci_comparisons <- list(
  c("N_1", "N_1"),
  c("N_10", "N_10"),
  c("N_100", "N_100"),
  c("N_1000", "N_1000"),
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Perform statistical comparisons and save results
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Filter data for the two loci
  data_x <- data %>% filter(Loci == loci_x) %>% pull(QstValue)
  data_y <- data %>% filter(Loci == loci_y) %>% pull(QstValue)
  
  # Perform KS Test
  if (length(data_x) > 1 && length(data_y) > 1) {
    ks_test <- ks.test(data_x, data_y)
    sink(ks_test_file, append = TRUE)
    cat("KS Test for", loci_x, "vs", loci_y, ":\n")
    print(ks_test)
    cat("\n")
    sink()
  }
  
  # Perform AD Test using kSamples
if (length(data_x) > 1 && length(data_y) > 1) {
  ad_test <- kSamples::ad.test(data_x, data_y)
  sink(ad_test_file, append = TRUE)
  cat("AD Test for", loci_x, "vs", loci_y, ":\n")
  print(ad_test)
  cat("\n")
  sink()
} else {
  sink(ad_test_file, append = TRUE)
  cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "\n\n")
  sink()
}
}

# Grouped data for ANOVA and T-Test
anova_data <- data %>%
  filter(Loci %in% unlist(loci_comparisons)) %>%
  group_by(Loci) %>%
  summarise(QstValues = list(QstValue), .groups = "drop") %>%
  unnest(cols = c(QstValues))

# Perform ANOVA
anova_results <- aov(QstValue ~ Loci, data = data)
sink(anova_file, append = TRUE)
cat("ANOVA Results:\n")
print(summary(anova_results))
cat("\n")
sink()

# Perform T-Test
t_test_results <- pairwise.t.test(
  data$QstValue,
  data$Loci,
  p.adjust.method = "bonferroni"
)
sink(ttest_file, append = TRUE)
cat("T-Test Results:\n")
print(t_test_results)
cat("\n")
sink()
# Define loci comparisons for QQ plots
qqplot_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Generate QQ plots for specified comparisons
for (comparison in qqplot_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Filter data for the two loci
  data_x <- data %>% filter(Loci == loci_x) %>% pull(QstValue)
  data_y <- data %>% filter(Loci == loci_y) %>% pull(QstValue)
  
  if (length(data_x) > 1 && length(data_y) > 1) {
    # Generate QQ plot
    qqplot_data <- data.frame(
      x = sort(data_x),
      y = sort(data_y)
    )
    
    qq_plot <- ggplot(qqplot_data, aes(x = x, y = y)) +
      geom_point(color = "blue") +
      geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
      labs(
        title = paste("QQ Plot:", loci_x, "vs", loci_y),
        x = paste(loci_x ),
        y = paste(loci_y)
      ) +
      theme_minimal() +
      coord_fixed()+
      scale_x_continuous(limits = c(0.0, 0.1)) +
      scale_y_continuous(limits = c(0.0, 0.1))
    
    # Save the QQ plot
    qqplot_file <- file.path(output_dir, paste0("QQ_Plot_", loci_x, "_vs_", loci_y, ".png"))
    ggsave(qqplot_file, qq_plot, width = 6, height = 6)
  } else {
    cat("Insufficient data for QQ Plot for", loci_x, "vs", loci_y, "\n")
  }
}

```
## Average over 10 iteration
```{r}
# Define loci comparisons
loci_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Create an output folder
output_folder <- "./result/norm/maf/average_qqplots"
if (!dir.exists(output_folder)) dir.create(output_folder)

# Output files for statistical results
ks_test_file <- file.path(output_folder, "ks_test_results.txt")
ad_test_file <- file.path(output_folder, "ad_test_results.txt")
anova_file <- file.path(output_folder, "anova_results.txt")
ttest_file <- file.path(output_folder, "t_test_results.txt")

# Initialize output files
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA and Tukey HSD Results\n")
cat("===========================\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("================\n\n")
sink()

# Loop over loci comparisons
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Average values over all replications for each replicate
  averaged_data <- do.call(rbind, lapply(names(norm_minor_replication[[1]]), function(replicate_name) {
    # Extract replicate data across all replications
    replicate_values <- do.call(rbind, lapply(names(norm_minor_replication), function(replication_name) {
      norm_minor_replication[[replication_name]][[replicate_name]]
    }))
    
    # Ensure data is numeric
    numeric_values <- as.data.frame(lapply(as.data.frame(replicate_values), as.numeric))
    
    # Compute averages for loci_x and loci_y
    data.frame(
      Replicate = replicate_name,
      x = mean(numeric_values[[loci_x]], na.rm = TRUE),
      y = mean(numeric_values[[loci_y]], na.rm = TRUE)
    )
  }))
  
  # Sort values for quantile-quantile plotting
  x_sorted <- sort(averaged_data$x, na.last = TRUE)
  y_sorted <- sort(averaged_data$y, na.last = TRUE)
  
  # Perform Kolmogorov-Smirnov Test
  ks_test <- ks.test(x_sorted, y_sorted)
  sink(ks_test_file, append = TRUE)
  cat("KS Test for", loci_x, "vs", loci_y, ":\n")
  print(ks_test)
  cat("\n")
  sink()
  
    # Perform Anderson-Darling Test using kSamples
  if (length(x_sorted) > 1 && length(y_sorted) > 1) {
    ad_test <- kSamples::ad.test(x_sorted, y_sorted)
    sink(ad_test_file, append = TRUE)
    cat("AD Test for", loci_x, "vs", loci_y, ":\n")
    print(ad_test)
    cat("\n")
    sink()
  } else {
    sink(ad_test_file, append = TRUE)
    cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "\n\n")
    sink()
  }

  
   # Combine data for ANOVA and t-tests
  combined_data <- data.frame(
    Group = rep(c(loci_x, loci_y), each = length(x_sorted)),
    Value = c(x_sorted, y_sorted)
  )
  
  # Perform ANOVA
  anova_results <- aov(Value ~ Group, data = combined_data)
  sink(anova_file, append = TRUE)
  cat("ANOVA Results for", loci_x, "vs", loci_y, ":\n")
  print(summary(anova_results))
  cat("\n")
  
  # Tukey's HSD Post-Hoc Test
  cat("Tukey HSD Results for", loci_x, "vs", loci_y, ":\n")
  tukey_results <- TukeyHSD(anova_results)
  print(tukey_results)
  cat("\n")
  sink()
  
  # Perform t-test
  t_test_results <- t.test(x_sorted, y_sorted)
  sink(ttest_file, append = TRUE)
  cat("T-Test Results for", loci_x, "vs", loci_y, ":\n")
  print(t_test_results)
  cat("\n")
  sink()
  
  # Create a data frame for plotting
  plot_data <- data.frame(x = x_sorted, y = y_sorted)
  
  # Generate QQ plot
  plot <- ggplot(data = plot_data, aes(x = y, y = x)) +
    geom_point(color = "blue") +
    geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
    labs(
      title = paste("Averaged QQ Plot:", loci_x, "vs", loci_y),
      x = paste( loci_y),
      y = paste( loci_x)
    ) +
    theme_minimal() +
    coord_fixed() +
    scale_x_continuous(limits = c(0.0, 0.04)) +
    scale_y_continuous(limits = c(0.0, 0.04))
  
  # Save the plot
  file_name <- file.path(output_folder, paste0("Averaged_QQ_Plot_", loci_x, "_vs_", loci_y, ".png"))
  ggsave(filename = file_name, plot = plot, width = 6, height = 4)
}
```

# Uniform distribution
## Without minor allele sampling
```{r}

loci_counts <- c(1, 10, 100, 1000)
uni_replication <- list()

for (number in 1:10) {
  #set.seed(seed_value + number)  # Ensure unique seed per replication
  qst_result_norm <- list()
  
  for (replicate in seq_along(data_numeric_list)) {
    print(paste0("Processing replicate: ", replicate, " replication: ", number))
    
    # Split replicate into 8 populations
    splited_pop <- split_into_pop(data_numeric_list[[replicate]])
    
    # Initialize Qst results for the replicate
    qst_resutl <- list()
    
    for (loci in loci_counts) {
      #set.seed(seed_value + number + loci + replicate)  # Unique seed for loci, replicate, and replication
      
      # Compute phenotype for the 8 populations
      phenotype <- phenotype_calc_uni(splited_pop, loci)
      qst <- Qst_cal(phenotype)
      qst_resutl[[paste0("N_", loci)]] <- qst
    }
    
    # Store Qst results for the replicate
    qst_result_norm[[paste0("replicate_", replicate)]] <- qst_resutl
  }
  
  # Store Qst results for the replication
  uni_replication[[paste0("replication_", number)]] <- qst_result_norm
}

```


### within replicate:
```{r}
# Define the output folder and create it if necessary
output_folder <- "./result/uni/wo_maf/within_replication_qqplot"
if (!dir.exists(output_folder)) {
  dir.create(output_folder, recursive = TRUE)  # Create folder if it doesn't exist
}

# Loci comparisons
loci_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Output files for statistical results
ks_test_file <- file.path(output_folder, "ks_test_results.txt")
ad_test_file <- file.path(output_folder, "ad_test_results.txt")
anova_file <- file.path(output_folder, "anova_results.txt")
ttest_file <- file.path(output_folder, "t_test_results.txt")

# Initialize file connections
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA and Tukey HSD Results\n")
cat("===========================\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("================\n\n")
sink()

# Loop over replications
for (replication_name in names(uni_replication)) {
  current_replication <- uni_replication[[replication_name]]  # Extract current replication
  
  # Initialize data for ANOVA and T-tests
  all_loci_values <- list()
  
  # Loop over loci comparisons
  for (comparison in loci_comparisons) {
    loci_x <- comparison[1]
    loci_y <- comparison[2]
    
    # Extract and combine data across all replicates for the loci sets
    combined_data <- do.call(rbind, lapply(names(current_replication), function(replicate_name) {
      replicate_data <- current_replication[[replicate_name]]
      data.frame(
        Replicate = replicate_name,
        x = replicate_data[[loci_x]],
        y = replicate_data[[loci_y]]
      )
    }))
    
    # Store data for ANOVA and T-tests
    all_loci_values[[loci_x]] <- combined_data$x
    all_loci_values[[loci_y]] <- combined_data$y
    
    # Perform KS Test
    ks_test <- ks.test(combined_data$x, combined_data$y)
    sink(ks_test_file, append = TRUE)
    cat("KS Test for", loci_x, "vs", loci_y, "in", replication_name, ":\n")
    print(ks_test)
    cat("\n")
    sink()
    
    # Perform AD Test using kSamples
if (length(combined_data$x) > 1 && length(combined_data$y) > 1) {
  ad_test <- kSamples::ad.test(combined_data$x, combined_data$y)
  sink(ad_test_file, append = TRUE)
  cat("AD Test for", loci_x, "vs", loci_y, "in", replication_name, ":\n")
  print(ad_test)
  cat("\n")
  sink()
} else {
  sink(ad_test_file, append = TRUE)
  cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "in", replication_name, "\n\n")
  sink()
}
    
    # Generate QQ plot
    x_sorted <- sort(combined_data$x, na.last = TRUE)
    y_sorted <- sort(combined_data$y, na.last = TRUE)
    plot_data <- data.frame(x = x_sorted, y = y_sorted)
    
    plot <- ggplot(data = plot_data, aes(x = y, y = x)) +
      geom_point(color = "blue") +
      geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
      labs(
        title = paste(loci_x, "vs", loci_y, "-", replication_name),
        x = paste(loci_y),
        y = paste(loci_x)
      ) +
      theme_minimal() +
      coord_fixed() +
      scale_x_continuous(limits = c(0.0, 0.1)) +
      scale_y_continuous(limits = c(0.0, 0.1))
    
    file_name <- file.path(output_folder, paste0("QQ_Plot_", loci_x, "_vs_", loci_y, "_", replication_name, ".png"))
    ggsave(filename = file_name, plot = plot, width = 6, height = 4)
  }
  
  # Combine data for ANOVA and T-tests
  loci_groups <- unlist(lapply(names(all_loci_values), function(loci) {
    rep(loci, length(all_loci_values[[loci]]))
  }))
  qst_values <- unlist(all_loci_values)
  data <- data.frame(
    LociGroup = factor(loci_groups, levels = names(all_loci_values)),
    QstValue = qst_values
  )
  
  # Perform ANOVA
  anova_results <- aov(QstValue ~ LociGroup, data = data)
  sink(anova_file, append = TRUE)
  cat("ANOVA Results for", replication_name, ":\n")
  print(summary(anova_results))
  cat("\n")
  
  # Tukey's HSD Post-Hoc Test
  cat("Tukey HSD Results for", replication_name, ":\n")
  tukey_results <- TukeyHSD(anova_results)
  print(tukey_results)
  cat("\n")
  sink()
  
  # Perform T-Test
  t_test_results <- pairwise.t.test(
    data$QstValue,
    data$LociGroup,
    p.adjust.method = "bonferroni"
  )
  sink(ttest_file, append = TRUE)
  cat("T-Test Results for", replication_name, ":\n")
  print(t_test_results)
  cat("\n")
  sink()
}
```
### all replicate
```{r}
# Set output directory
output_dir <- "./result/uni/wo_maf/between_replication_qqplot"
if (!dir.exists(output_dir)) dir.create(output_dir)

# Output files for statistical results
ks_test_file <- file.path(output_dir, "ks_test_results.txt")
ad_test_file <- file.path(output_dir, "ad_test_results.txt")
anova_file <- file.path(output_dir, "anova_results.txt")
ttest_file <- file.path(output_dir, "t_test_results.txt")

# Initialize file connections
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA Results\n")
cat("=============\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("==============\n\n")
sink()


# Assuming `replication` is the nested structure
data <- flatten_replication_data(uni_replication)

# Define loci comparisons
loci_comparisons <- list(
  c("N_1", "N_1"),
  c("N_10", "N_10"),
  c("N_100", "N_100"),
  c("N_1000", "N_1000"),
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Perform statistical comparisons and save results
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Filter data for the two loci
  data_x <- data %>% filter(Loci == loci_x) %>% pull(QstValue)
  data_y <- data %>% filter(Loci == loci_y) %>% pull(QstValue)
  
  # Perform KS Test
  if (length(data_x) > 1 && length(data_y) > 1) {
    ks_test <- ks.test(data_x, data_y)
    sink(ks_test_file, append = TRUE)
    cat("KS Test for", loci_x, "vs", loci_y, ":\n")
    print(ks_test)
    cat("\n")
    sink()
  }
  
  # Perform AD Test using kSamples
if (length(data_x) > 1 && length(data_y) > 1) {
  ad_test <- kSamples::ad.test(data_x, data_y)
  sink(ad_test_file, append = TRUE)
  cat("AD Test for", loci_x, "vs", loci_y, ":\n")
  print(ad_test)
  cat("\n")
  sink()
} else {
  sink(ad_test_file, append = TRUE)
  cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "\n\n")
  sink()
}
}

# Grouped data for ANOVA and T-Test
anova_data <- data %>%
  filter(Loci %in% unlist(loci_comparisons)) %>%
  group_by(Loci) %>%
  summarise(QstValues = list(QstValue), .groups = "drop") %>%
  unnest(cols = c(QstValues))

# Perform ANOVA
anova_results <- aov(QstValue ~ Loci, data = data)
sink(anova_file, append = TRUE)
cat("ANOVA Results:\n")
print(summary(anova_results))
cat("\n")
sink()

# Perform T-Test
t_test_results <- pairwise.t.test(
  data$QstValue,
  data$Loci,
  p.adjust.method = "bonferroni"
)
sink(ttest_file, append = TRUE)
cat("T-Test Results:\n")
print(t_test_results)
cat("\n")
sink()
# Define loci comparisons for QQ plots
qqplot_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Generate QQ plots for specified comparisons
for (comparison in qqplot_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Filter data for the two loci
  data_x <- data %>% filter(Loci == loci_x) %>% pull(QstValue)
  data_y <- data %>% filter(Loci == loci_y) %>% pull(QstValue)
  
  if (length(data_x) > 1 && length(data_y) > 1) {
    # Generate QQ plot
    qqplot_data <- data.frame(
      x = sort(data_x),
      y = sort(data_y)
    )
    
    qq_plot <- ggplot(qqplot_data, aes(x = x, y = y)) +
      geom_point(color = "blue") +
      geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
      labs(
        title = paste("QQ Plot:", loci_x, "vs", loci_y),
        x = paste(loci_x ),
        y = paste(loci_y)
      ) +
      theme_minimal() +
      coord_fixed()+
      scale_x_continuous(limits = c(0.0, 0.1)) +
      scale_y_continuous(limits = c(0.0, 0.1))
    
    # Save the QQ plot
    qqplot_file <- file.path(output_dir, paste0("QQ_Plot_", loci_x, "_vs_", loci_y, ".png"))
    ggsave(qqplot_file, qq_plot, width = 6, height = 6)
  } else {
    cat("Insufficient data for QQ Plot for", loci_x, "vs", loci_y, "\n")
  }
}

```
### average over 10 iterations
```{r}
# Define loci comparisons
loci_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Create an output folder
output_folder <- "./result/uni/wo_maf//average_qqplots"
if (!dir.exists(output_folder)) dir.create(output_folder)

# Output files for statistical results
ks_test_file <- file.path(output_folder, "ks_test_results.txt")
ad_test_file <- file.path(output_folder, "ad_test_results.txt")
anova_file <- file.path(output_folder, "anova_results.txt")
ttest_file <- file.path(output_folder, "t_test_results.txt")

# Initialize output files
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA and Tukey HSD Results\n")
cat("===========================\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("================\n\n")
sink()

# Loop over loci comparisons
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Average values over all replications for each replicate
  averaged_data <- do.call(rbind, lapply(names(uni_replication[[1]]), function(replicate_name) {
    # Extract replicate data across all replications
    replicate_values <- do.call(rbind, lapply(names(uni_replication), function(replication_name) {
      uni_replication[[replication_name]][[replicate_name]]
    }))
    
    # Ensure data is numeric
    numeric_values <- as.data.frame(lapply(as.data.frame(replicate_values), as.numeric))
    
    # Compute averages for loci_x and loci_y
    data.frame(
      Replicate = replicate_name,
      x = mean(numeric_values[[loci_x]], na.rm = TRUE),
      y = mean(numeric_values[[loci_y]], na.rm = TRUE)
    )
  }))
  
  # Sort values for quantile-quantile plotting
  x_sorted <- sort(averaged_data$x, na.last = TRUE)
  y_sorted <- sort(averaged_data$y, na.last = TRUE)
  
  # Perform Kolmogorov-Smirnov Test
  ks_test <- ks.test(x_sorted, y_sorted)
  sink(ks_test_file, append = TRUE)
  cat("KS Test for", loci_x, "vs", loci_y, ":\n")
  print(ks_test)
  cat("\n")
  sink()
  
  # Perform Anderson-Darling Test
if (length(x_sorted) > 1 && length(y_sorted) > 1) {
  ad_test <- kSamples::ad.test(x_sorted, y_sorted)
  sink(ad_test_file, append = TRUE)
  cat("AD Test for", loci_x, "vs", loci_y, ":\n")
  print(ad_test)
  cat("\n")
  sink()
} else {
  sink(ad_test_file, append = TRUE)
  cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "\n\n")
  sink()
}
  
   # Combine data for ANOVA and t-tests
  combined_data <- data.frame(
    Group = rep(c(loci_x, loci_y), each = length(x_sorted)),
    Value = c(x_sorted, y_sorted)
  )
  
  # Perform ANOVA
  anova_results <- aov(Value ~ Group, data = combined_data)
  sink(anova_file, append = TRUE)
  cat("ANOVA Results for", loci_x, "vs", loci_y, ":\n")
  print(summary(anova_results))
  cat("\n")
  
  # Tukey's HSD Post-Hoc Test
  cat("Tukey HSD Results for", loci_x, "vs", loci_y, ":\n")
  tukey_results <- TukeyHSD(anova_results)
  print(tukey_results)
  cat("\n")
  sink()
  
  # Perform t-test
  t_test_results <- t.test(x_sorted, y_sorted)
  sink(ttest_file, append = TRUE)
  cat("T-Test Results for", loci_x, "vs", loci_y, ":\n")
  print(t_test_results)
  cat("\n")
  sink()
  
  # Create a data frame for plotting
  plot_data <- data.frame(x = x_sorted, y = y_sorted)
  
  # Generate QQ plot
  plot <- ggplot(data = plot_data, aes(x = y, y = x)) +
    geom_point(color = "blue") +
    geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
    labs(
      title = paste("Averaged QQ Plot:", loci_x, "vs", loci_y),
      x = paste(loci_y),
      y = paste(loci_x)
    ) +
    theme_minimal() +
    coord_fixed() +
    scale_x_continuous(limits = c(0.0, 0.06)) +
    scale_y_continuous(limits = c(0.0, 0.06))
  
  # Save the plot
  file_name <- file.path(output_folder, paste0("Averaged_QQ_Plot_", loci_x, "_vs_", loci_y, ".png"))
  ggsave(filename = file_name, plot = plot, width = 6, height = 4)
}
```


## With minor allele sampling
```{r}
loci_counts <- c(1, 10, 100, 1000)
uni_minor_replication <- list()

for (number in 1:10) {
  #set.seed(seed_value + number)  # Ensure unique seed per replication
  qst_result_norm <- list()
  
  for (replicate in seq_along(minor_data_list)) {
    print(paste0("Processing replicate: ", replicate, " replication: ", number))
    
    # Split replicate into 8 populations
    splited_pop <- split_into_pop(minor_data_list[[replicate]])
    
    # Initialize Qst results for the replicate
    qst_resutl <- list()
    
    for (loci in loci_counts) {
      #set.seed(seed_value + number + loci + replicate)  # Unique seed for loci, replicate, and replication
      
      # Compute phenotype for the 8 populations
      phenotype <- phenotype_calc_uni(splited_pop, loci)
      qst <- Qst_cal(phenotype)
      qst_resutl[[paste0("N_", loci)]] <- qst
    }
    
    # Store Qst results for the replicate
    qst_result_norm[[paste0("replicate_", replicate)]] <- qst_resutl
  }
  
  # Store Qst results for the replication
  uni_minor_replication[[paste0("replication_", number)]] <- qst_result_norm
}

```

### within replication
```{r}
# Define the output folder and create it if necessary
output_folder <- "./result/uni/maf/within_replication_qqplot"
if (!dir.exists(output_folder)) {
  dir.create(output_folder, recursive = TRUE)  # Create folder if it doesn't exist
}

# Loci comparisons
loci_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Output files for statistical results
ks_test_file <- file.path(output_folder, "ks_test_results.txt")
ad_test_file <- file.path(output_folder, "ad_test_results.txt")
anova_file <- file.path(output_folder, "anova_results.txt")
ttest_file <- file.path(output_folder, "t_test_results.txt")

# Initialize file connections
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA and Tukey HSD Results\n")
cat("===========================\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("================\n\n")
sink()

# Loop over replications
for (replication_name in names(uni_minor_replication)) {
  current_replication <- uni_minor_replication[[replication_name]]  # Extract current replication
  
  # Initialize data for ANOVA and T-tests
  all_loci_values <- list()
  
  # Loop over loci comparisons
  for (comparison in loci_comparisons) {
    loci_x <- comparison[1]
    loci_y <- comparison[2]
    
    # Extract and combine data across all replicates for the loci sets
    combined_data <- do.call(rbind, lapply(names(current_replication), function(replicate_name) {
      replicate_data <- current_replication[[replicate_name]]
      data.frame(
        Replicate = replicate_name,
        x = replicate_data[[loci_x]],
        y = replicate_data[[loci_y]]
      )
    }))
    
    # Store data for ANOVA and T-tests
    all_loci_values[[loci_x]] <- combined_data$x
    all_loci_values[[loci_y]] <- combined_data$y
    
    # Perform KS Test
    ks_test <- ks.test(combined_data$x, combined_data$y)
    sink(ks_test_file, append = TRUE)
    cat("KS Test for", loci_x, "vs", loci_y, "in", replication_name, ":\n")
    print(ks_test)
    cat("\n")
    sink()
    
    # Perform AD Test
    if (length(combined_data$x) > 1 && length(combined_data$y) > 1) {
  ad_test <- kSamples::ad.test(combined_data$x, combined_data$y)
  sink(ad_test_file, append = TRUE)
  cat("AD Test for", loci_x, "vs", loci_y, "in", replication_name, ":\n")
  print(ad_test)
  cat("\n")
  sink()
} else {
  sink(ad_test_file, append = TRUE)
  cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "in", replication_name, "\n\n")
  sink()
}
    
    # Generate QQ plot
    x_sorted <- sort(combined_data$x, na.last = TRUE)
    y_sorted <- sort(combined_data$y, na.last = TRUE)
    plot_data <- data.frame(x = x_sorted, y = y_sorted)
    
    plot <- ggplot(data = plot_data, aes(x = y, y = x)) +
      geom_point(color = "blue") +
      geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
      labs(
        title = paste(loci_x, "vs", loci_y, "-", replication_name),
        x = paste(loci_y),
        y = paste(loci_x)
      ) +
      theme_minimal() +
      coord_fixed() +
      scale_x_continuous(limits = c(0.0, 0.1)) +
      scale_y_continuous(limits = c(0.0, 0.1))
    
    file_name <- file.path(output_folder, paste0("QQ_Plot_", loci_x, "_vs_", loci_y, "_", replication_name, ".png"))
    ggsave(filename = file_name, plot = plot, width = 6, height = 4)
  }
  
  # Combine data for ANOVA and T-tests
  loci_groups <- unlist(lapply(names(all_loci_values), function(loci) {
    rep(loci, length(all_loci_values[[loci]]))
  }))
  qst_values <- unlist(all_loci_values)
  data <- data.frame(
    LociGroup = factor(loci_groups, levels = names(all_loci_values)),
    QstValue = qst_values
  )
  
  # Perform ANOVA
  anova_results <- aov(QstValue ~ LociGroup, data = data)
  sink(anova_file, append = TRUE)
  cat("ANOVA Results for", replication_name, ":\n")
  print(summary(anova_results))
  cat("\n")
  
  # Tukey's HSD Post-Hoc Test
  cat("Tukey HSD Results for", replication_name, ":\n")
  tukey_results <- TukeyHSD(anova_results)
  print(tukey_results)
  cat("\n")
  sink()
  
  # Perform T-Test
  t_test_results <- pairwise.t.test(
    data$QstValue,
    data$LociGroup,
    p.adjust.method = "bonferroni"
  )
  sink(ttest_file, append = TRUE)
  cat("T-Test Results for", replication_name, ":\n")
  print(t_test_results)
  cat("\n")
  sink()
}
```
### between replication
```{r}
# Set output directory
output_dir <- "./result/uni/maf/between_replication_qqplot/"
if (!dir.exists(output_dir)) dir.create(output_dir)

# Output files for statistical results
ks_test_file <- file.path(output_dir, "ks_test_results.txt")
ad_test_file <- file.path(output_dir, "ad_test_results.txt")
anova_file <- file.path(output_dir, "anova_results.txt")
ttest_file <- file.path(output_dir, "t_test_results.txt")

# Initialize file connections
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA Results\n")
cat("=============\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("==============\n\n")
sink()


# Assuming `replication` is the nested structure
data <- flatten_replication_data(uni_minor_replication)

# Define loci comparisons
loci_comparisons <- list(
  c("N_1", "N_1"),
  c("N_10", "N_10"),
  c("N_100", "N_100"),
  c("N_1000", "N_1000"),
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Perform statistical comparisons and save results
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Filter data for the two loci
  data_x <- data %>% filter(Loci == loci_x) %>% pull(QstValue)
  data_y <- data %>% filter(Loci == loci_y) %>% pull(QstValue)
  
  # Perform KS Test
  if (length(data_x) > 1 && length(data_y) > 1) {
    ks_test <- ks.test(data_x, data_y)
    sink(ks_test_file, append = TRUE)
    cat("KS Test for", loci_x, "vs", loci_y, ":\n")
    print(ks_test)
    cat("\n")
    sink()
  }
  
  # Perform AD Test using kSamples
if (length(data_x) > 1 && length(data_y) > 1) {
  ad_test <- kSamples::ad.test(data_x, data_y)
  sink(ad_test_file, append = TRUE)
  cat("AD Test for", loci_x, "vs", loci_y, ":\n")
  print(ad_test)
  cat("\n")
  sink()
} else {
  sink(ad_test_file, append = TRUE)
  cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "\n\n")
  sink()
}
}

# Grouped data for ANOVA and T-Test
anova_data <- data %>%
  filter(Loci %in% unlist(loci_comparisons)) %>%
  group_by(Loci) %>%
  summarise(QstValues = list(QstValue), .groups = "drop") %>%
  unnest(cols = c(QstValues))

# Perform ANOVA
anova_results <- aov(QstValue ~ Loci, data = data)
sink(anova_file, append = TRUE)
cat("ANOVA Results:\n")
print(summary(anova_results))
cat("\n")
sink()

# Perform T-Test
t_test_results <- pairwise.t.test(
  data$QstValue,
  data$Loci,
  p.adjust.method = "bonferroni"
)
sink(ttest_file, append = TRUE)
cat("T-Test Results:\n")
print(t_test_results)
cat("\n")
sink()
# Define loci comparisons for QQ plots
qqplot_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Generate QQ plots for specified comparisons
for (comparison in qqplot_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Filter data for the two loci
  data_x <- data %>% filter(Loci == loci_x) %>% pull(QstValue)
  data_y <- data %>% filter(Loci == loci_y) %>% pull(QstValue)
  
  if (length(data_x) > 1 && length(data_y) > 1) {
    # Generate QQ plot
    qqplot_data <- data.frame(
      x = sort(data_x),
      y = sort(data_y)
    )
    
    qq_plot <- ggplot(qqplot_data, aes(x = x, y = y)) +
      geom_point(color = "blue") +
      geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
      labs(
        title = paste("QQ Plot:", loci_x, "vs", loci_y),
        x = paste(loci_x ),
        y = paste(loci_y)
      ) +
      theme_minimal() +
      coord_fixed()+
      scale_x_continuous(limits = c(0.0, 0.1)) +
      scale_y_continuous(limits = c(0.0, 0.1))
    
    # Save the QQ plot
    qqplot_file <- file.path(output_dir, paste0("QQ_Plot_", loci_x, "_vs_", loci_y, ".png"))
    ggsave(qqplot_file, qq_plot, width = 6, height = 6)
  } else {
    cat("Insufficient data for QQ Plot for", loci_x, "vs", loci_y, "\n")
  }
}
```
### average over 10 replication
```{r}
# Define loci comparisons
loci_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Create an output folder
output_folder <- "./result/uni/maf/average_qqplots"
if (!dir.exists(output_folder)) dir.create(output_folder)

# Output files for statistical results
ks_test_file <- file.path(output_folder, "ks_test_results.txt")
ad_test_file <- file.path(output_folder, "ad_test_results.txt")
anova_file <- file.path(output_folder, "anova_results.txt")
ttest_file <- file.path(output_folder, "t_test_results.txt")

# Initialize output files
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA and Tukey HSD Results\n")
cat("===========================\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("================\n\n")
sink()

# Loop over loci comparisons
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Average values over all replications for each replicate
  averaged_data <- do.call(rbind, lapply(names(uni_minor_replication[[1]]), function(replicate_name) {
    # Extract replicate data across all replications
    replicate_values <- do.call(rbind, lapply(names(uni_minor_replication), function(replication_name) {
      uni_minor_replication[[replication_name]][[replicate_name]]
    }))
    
    # Ensure data is numeric
    numeric_values <- as.data.frame(lapply(as.data.frame(replicate_values), as.numeric))
    
    # Compute averages for loci_x and loci_y
    data.frame(
      Replicate = replicate_name,
      x = mean(numeric_values[[loci_x]], na.rm = TRUE),
      y = mean(numeric_values[[loci_y]], na.rm = TRUE)
    )
  }))
  
  # Sort values for quantile-quantile plotting
  x_sorted <- sort(averaged_data$x, na.last = TRUE)
  y_sorted <- sort(averaged_data$y, na.last = TRUE)
  
  # Perform Kolmogorov-Smirnov Test
  ks_test <- ks.test(x_sorted, y_sorted)
  sink(ks_test_file, append = TRUE)
  cat("KS Test for", loci_x, "vs", loci_y, ":\n")
  print(ks_test)
  cat("\n")
  sink()
  
  # Perform Anderson-Darling Test
  if (length(x_sorted) > 1 && length(y_sorted) > 1) {
  ad_test <- kSamples::ad.test(x_sorted, y_sorted)
  sink(ad_test_file, append = TRUE)
  cat("AD Test for", loci_x, "vs", loci_y, ":\n")
  print(ad_test)
  cat("\n")
  sink()
} else {
  sink(ad_test_file, append = TRUE)
  cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "\n\n")
  sink()
}
  
   # Combine data for ANOVA and t-tests
  combined_data <- data.frame(
    Group = rep(c(loci_x, loci_y), each = length(x_sorted)),
    Value = c(x_sorted, y_sorted)
  )
  
  # Perform ANOVA
  anova_results <- aov(Value ~ Group, data = combined_data)
  sink(anova_file, append = TRUE)
  cat("ANOVA Results for", loci_x, "vs", loci_y, ":\n")
  print(summary(anova_results))
  cat("\n")
  
  # Tukey's HSD Post-Hoc Test
  cat("Tukey HSD Results for", loci_x, "vs", loci_y, ":\n")
  tukey_results <- TukeyHSD(anova_results)
  print(tukey_results)
  cat("\n")
  sink()
  
  # Perform t-test
  t_test_results <- t.test(x_sorted, y_sorted)
  sink(ttest_file, append = TRUE)
  cat("T-Test Results for", loci_x, "vs", loci_y, ":\n")
  print(t_test_results)
  cat("\n")
  sink()
  
  # Create a data frame for plotting
  plot_data <- data.frame(x = x_sorted, y = y_sorted)
  
  # Generate QQ plot
  plot <- ggplot(data = plot_data, aes(x = y, y = x)) +
    geom_point(color = "blue") +
    geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
    labs(
      title = paste("Averaged QQ Plot:", loci_x, "vs", loci_y),
      x = paste( loci_y),
      y = paste( loci_x)
    ) +
    theme_minimal() +
    coord_fixed() +
    scale_x_continuous(limits = c(0.0, 0.04)) +
    scale_y_continuous(limits = c(0.0, 0.04))
  
  # Save the plot
  file_name <- file.path(output_folder, paste0("Averaged_QQ_Plot_", loci_x, "_vs_", loci_y, ".png"))
  ggsave(filename = file_name, plot = plot, width = 6, height = 4)
}

```
# L-shaped
```{r}
# type of distribution used
test <- rpareto(1000, scale = 0.1, shape = 2)

hist(test, breaks = 1000, col = "lightgreen", main = "Pareto Distribution of Effect Sizes",
     xlab = "Effect Size", ylab = "Frequency", probability = TRUE)
#lines(density(test), col = "darkgreen", lwd = 2)
```
## without maf
```{r}
loci_counts <- c(1, 10, 100, 1000)
l_replication <- list()

for (number in 1:10) {
  #set.seed(seed_value + number)  # Ensure unique seed per replication
  qst_result_norm <- list()
  
  for (replicate in seq_along(data_numeric_list)) {
    print(paste0("Processing replicate: ", replicate, " replication: ", number))
    
    # Split replicate into 8 populations
    splited_pop <- split_into_pop(data_numeric_list[[replicate]])
    
    # Initialize Qst results for the replicate
    qst_resutl <- list()
    
    for (loci in loci_counts) {
      #set.seed(seed_value + number + loci + replicate)  # Unique seed for loci, replicate, and replication
      
      # Compute phenotype for the 8 populations
      phenotype <- phenotype_calc_l(splited_pop, loci)
      qst <- Qst_cal(phenotype)
      qst_resutl[[paste0("N_", loci)]] <- qst
    }
    
    # Store Qst results for the replicate
    qst_result_norm[[paste0("replicate_", replicate)]] <- qst_resutl
  }
  
  # Store Qst results for the replication
  l_replication[[paste0("replication_", number)]] <- qst_result_norm
}
```
### within replicate
```{r}
# Define the output folder and create it if necessary
output_folder <- "./result/l/wo_maf/within_replication_qqplot"
if (!dir.exists(output_folder)) {
  dir.create(output_folder, recursive = TRUE)  # Create folder if it doesn't exist
}

# Loci comparisons
loci_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Output files for statistical results
ks_test_file <- file.path(output_folder, "ks_test_results.txt")
ad_test_file <- file.path(output_folder, "ad_test_results.txt")
anova_file <- file.path(output_folder, "anova_results.txt")
ttest_file <- file.path(output_folder, "t_test_results.txt")

# Initialize file connections
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA and Tukey HSD Results\n")
cat("===========================\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("================\n\n")
sink()

# Loop over replications
for (replication_name in names(l_replication)) {
  current_replication <- l_replication[[replication_name]]  # Extract current replication
  
  # Initialize data for ANOVA and T-tests
  all_loci_values <- list()
  
  # Loop over loci comparisons
  for (comparison in loci_comparisons) {
    loci_x <- comparison[1]
    loci_y <- comparison[2]
    
    # Extract and combine data across all replicates for the loci sets
    combined_data <- do.call(rbind, lapply(names(current_replication), function(replicate_name) {
      replicate_data <- current_replication[[replicate_name]]
      data.frame(
        Replicate = replicate_name,
        x = replicate_data[[loci_x]],
        y = replicate_data[[loci_y]]
      )
    }))
    
    # Store data for ANOVA and T-tests
    all_loci_values[[loci_x]] <- combined_data$x
    all_loci_values[[loci_y]] <- combined_data$y
    
    # Perform KS Test
    ks_test <- ks.test(combined_data$x, combined_data$y)
    sink(ks_test_file, append = TRUE)
    cat("KS Test for", loci_x, "vs", loci_y, "in", replication_name, ":\n")
    print(ks_test)
    cat("\n")
    sink()
    
    # Perform AD Test
    if (length(combined_data$x) > 1 && length(combined_data$y) > 1) {
  ad_test <- kSamples::ad.test(combined_data$x, combined_data$y)
  sink(ad_test_file, append = TRUE)
  cat("AD Test for", loci_x, "vs", loci_y, "in", replication_name, ":\n")
  print(ad_test)
  cat("\n")
  sink()
} else {
  sink(ad_test_file, append = TRUE)
  cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "in", replication_name, "\n\n")
  sink()
}
    
    # Generate QQ plot
    x_sorted <- sort(combined_data$x, na.last = TRUE)
    y_sorted <- sort(combined_data$y, na.last = TRUE)
    plot_data <- data.frame(x = x_sorted, y = y_sorted)
    
    plot <- ggplot(data = plot_data, aes(x = y, y = x)) +
      geom_point(color = "blue") +
      geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
      labs(
        title = paste(loci_x, "vs", loci_y, "-", replication_name),
        x = paste(loci_y),
        y = paste(loci_x)
      ) +
      theme_minimal() +
      coord_fixed() +
      scale_x_continuous(limits = c(0.0, 0.1)) +
      scale_y_continuous(limits = c(0.0, 0.1))
    
    file_name <- file.path(output_folder, paste0("QQ_Plot_", loci_x, "_vs_", loci_y, "_", replication_name, ".png"))
    ggsave(filename = file_name, plot = plot, width = 6, height = 4)
  }
  
  # Combine data for ANOVA and T-tests
  loci_groups <- unlist(lapply(names(all_loci_values), function(loci) {
    rep(loci, length(all_loci_values[[loci]]))
  }))
  qst_values <- unlist(all_loci_values)
  data <- data.frame(
    LociGroup = factor(loci_groups, levels = names(all_loci_values)),
    QstValue = qst_values
  )
  
  # Perform ANOVA
  anova_results <- aov(QstValue ~ LociGroup, data = data)
  sink(anova_file, append = TRUE)
  cat("ANOVA Results for", replication_name, ":\n")
  print(summary(anova_results))
  cat("\n")
  
  # Tukey's HSD Post-Hoc Test
  cat("Tukey HSD Results for", replication_name, ":\n")
  tukey_results <- TukeyHSD(anova_results)
  print(tukey_results)
  cat("\n")
  sink()
  
  # Perform T-Test
  t_test_results <- pairwise.t.test(
    data$QstValue,
    data$LociGroup,
    p.adjust.method = "bonferroni"
  )
  sink(ttest_file, append = TRUE)
  cat("T-Test Results for", replication_name, ":\n")
  print(t_test_results)
  cat("\n")
  sink()
}
```

### between
```{r}
# Set output directory
output_dir <- "./result/l/wo_maf/between_replication_qqplot/"
if (!dir.exists(output_dir)) dir.create(output_dir)

# Output files for statistical results
ks_test_file <- file.path(output_dir, "ks_test_results.txt")
ad_test_file <- file.path(output_dir, "ad_test_results.txt")
anova_file <- file.path(output_dir, "anova_results.txt")
ttest_file <- file.path(output_dir, "t_test_results.txt")

# Initialize file connections
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA Results\n")
cat("=============\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("==============\n\n")
sink()


# Assuming `replication` is the nested structure
data <- flatten_replication_data(l_replication)

# Define loci comparisons
loci_comparisons <- list(
  c("N_1", "N_1"),
  c("N_10", "N_10"),
  c("N_100", "N_100"),
  c("N_1000", "N_1000"),
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Perform statistical comparisons and save results
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Filter data for the two loci
  data_x <- data %>% filter(Loci == loci_x) %>% pull(QstValue)
  data_y <- data %>% filter(Loci == loci_y) %>% pull(QstValue)
  
  # Perform KS Test
  if (length(data_x) > 1 && length(data_y) > 1) {
    ks_test <- ks.test(data_x, data_y)
    sink(ks_test_file, append = TRUE)
    cat("KS Test for", loci_x, "vs", loci_y, ":\n")
    print(ks_test)
    cat("\n")
    sink()
  }
  
  # Perform AD Test using kSamples
if (length(data_x) > 1 && length(data_y) > 1) {
  ad_test <- kSamples::ad.test(data_x, data_y)
  sink(ad_test_file, append = TRUE)
  cat("AD Test for", loci_x, "vs", loci_y, ":\n")
  print(ad_test)
  cat("\n")
  sink()
} else {
  sink(ad_test_file, append = TRUE)
  cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "\n\n")
  sink()
}
}

# Grouped data for ANOVA and T-Test
anova_data <- data %>%
  filter(Loci %in% unlist(loci_comparisons)) %>%
  group_by(Loci) %>%
  summarise(QstValues = list(QstValue), .groups = "drop") %>%
  unnest(cols = c(QstValues))

# Perform ANOVA
anova_results <- aov(QstValue ~ Loci, data = data)
sink(anova_file, append = TRUE)
cat("ANOVA Results:\n")
print(summary(anova_results))
cat("\n")
sink()

# Perform T-Test
t_test_results <- pairwise.t.test(
  data$QstValue,
  data$Loci,
  p.adjust.method = "bonferroni"
)
sink(ttest_file, append = TRUE)
cat("T-Test Results:\n")
print(t_test_results)
cat("\n")
sink()
# Define loci comparisons for QQ plots
qqplot_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Generate QQ plots for specified comparisons
for (comparison in qqplot_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Filter data for the two loci
  data_x <- data %>% filter(Loci == loci_x) %>% pull(QstValue)
  data_y <- data %>% filter(Loci == loci_y) %>% pull(QstValue)
  
  if (length(data_x) > 1 && length(data_y) > 1) {
    # Generate QQ plot
    qqplot_data <- data.frame(
      x = sort(data_x),
      y = sort(data_y)
    )
    
    qq_plot <- ggplot(qqplot_data, aes(x = x, y = y)) +
      geom_point(color = "blue") +
      geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
      labs(
        title = paste("QQ Plot:", loci_x, "vs", loci_y),
        x = paste(loci_x ),
        y = paste(loci_y)
      ) +
      theme_minimal() +
      coord_fixed()+
      scale_x_continuous(limits = c(0.0, 0.1)) +
      scale_y_continuous(limits = c(0.0, 0.1))
    
    # Save the QQ plot
    qqplot_file <- file.path(output_dir, paste0("QQ_Plot_", loci_x, "_vs_", loci_y, ".png"))
    ggsave(qqplot_file, qq_plot, width = 6, height = 6)
  } else {
    cat("Insufficient data for QQ Plot for", loci_x, "vs", loci_y, "\n")
  }
}

```
### average over replication
```{r}
# Define loci comparisons
loci_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Create an output folder
output_folder <- "./result/l/wo_maf//average_qqplots"
if (!dir.exists(output_folder)) dir.create(output_folder)

# Output files for statistical results
ks_test_file <- file.path(output_folder, "ks_test_results.txt")
ad_test_file <- file.path(output_folder, "ad_test_results.txt")
anova_file <- file.path(output_folder, "anova_results.txt")
ttest_file <- file.path(output_folder, "t_test_results.txt")

# Initialize output files
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA and Tukey HSD Results\n")
cat("===========================\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("================\n\n")
sink()

# Loop over loci comparisons
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Average values over all replications for each replicate
  averaged_data <- do.call(rbind, lapply(names(l_replication[[1]]), function(replicate_name) {
    # Extract replicate data across all replications
    replicate_values <- do.call(rbind, lapply(names(l_replication), function(replication_name) {
      l_replication[[replication_name]][[replicate_name]]
    }))
    
    # Ensure data is numeric
    numeric_values <- as.data.frame(lapply(as.data.frame(replicate_values), as.numeric))
    
    # Compute averages for loci_x and loci_y
    data.frame(
      Replicate = replicate_name,
      x = mean(numeric_values[[loci_x]], na.rm = TRUE),
      y = mean(numeric_values[[loci_y]], na.rm = TRUE)
    )
  }))
  
  # Sort values for quantile-quantile plotting
  x_sorted <- sort(averaged_data$x, na.last = TRUE)
  y_sorted <- sort(averaged_data$y, na.last = TRUE)
  
  # Perform Kolmogorov-Smirnov Test
  ks_test <- ks.test(x_sorted, y_sorted)
  sink(ks_test_file, append = TRUE)
  cat("KS Test for", loci_x, "vs", loci_y, ":\n")
  print(ks_test)
  cat("\n")
  sink()
  
  # Perform Anderson-Darling Test
  if (length(x_sorted) > 1 && length(y_sorted) > 1) {
  ad_test <- kSamples::ad.test(x_sorted, y_sorted)
  sink(ad_test_file, append = TRUE)
  cat("AD Test for", loci_x, "vs", loci_y, ":\n")
  print(ad_test)
  cat("\n")
  sink()
} else {
  sink(ad_test_file, append = TRUE)
  cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "\n\n")
  sink()
}
  
   # Combine data for ANOVA and t-tests
  combined_data <- data.frame(
    Group = rep(c(loci_x, loci_y), each = length(x_sorted)),
    Value = c(x_sorted, y_sorted)
  )
  
  # Perform ANOVA
  anova_results <- aov(Value ~ Group, data = combined_data)
  sink(anova_file, append = TRUE)
  cat("ANOVA Results for", loci_x, "vs", loci_y, ":\n")
  print(summary(anova_results))
  cat("\n")
  
  # Tukey's HSD Post-Hoc Test
  cat("Tukey HSD Results for", loci_x, "vs", loci_y, ":\n")
  tukey_results <- TukeyHSD(anova_results)
  print(tukey_results)
  cat("\n")
  sink()
  
  # Perform t-test
  t_test_results <- t.test(x_sorted, y_sorted)
  sink(ttest_file, append = TRUE)
  cat("T-Test Results for", loci_x, "vs", loci_y, ":\n")
  print(t_test_results)
  cat("\n")
  sink()
  
  # Create a data frame for plotting
  plot_data <- data.frame(x = x_sorted, y = y_sorted)
  
  # Generate QQ plot
  plot <- ggplot(data = plot_data, aes(x = y, y = x)) +
    geom_point(color = "blue") +
    geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
    labs(
      title = paste("Averaged QQ Plot:", loci_x, "vs", loci_y),
      x = paste(loci_y),
      y = paste(loci_x)
    ) +
    theme_minimal() +
    coord_fixed() +
    scale_x_continuous(limits = c(0.01, 0.04)) +
    scale_y_continuous(limits = c(0.01, 0.04))
  
  # Save the plot
  file_name <- file.path(output_folder, paste0("Averaged_QQ_Plot_", loci_x, "_vs_", loci_y, ".png"))
  ggsave(filename = file_name, plot = plot, width = 6, height = 4)
}
```



## with maf
```{r}
loci_counts <- c(1, 10, 100, 1000)
l_minor_replication <- list()

for (number in 1:10) {
  #set.seed(seed_value + number)  # Ensure unique seed per replication
  qst_result_norm <- list()
  
  for (replicate in seq_along(minor_data_list)) {
    print(paste0("Processing replicate: ", replicate, " replication: ", number))
    
    # Split replicate into 8 populations
    splited_pop <- split_into_pop(minor_data_list[[replicate]])
    
    # Initialize Qst results for the replicate
    qst_resutl <- list()
    
    for (loci in loci_counts) {
      #set.seed(seed_value + number + loci + replicate)  # Unique seed for loci, replicate, and replication
      
      # Compute phenotype for the 8 populations
      phenotype <- phenotype_calc_l(splited_pop, loci)
      qst <- Qst_cal(phenotype)
      qst_resutl[[paste0("N_", loci)]] <- qst
    }
    
    # Store Qst results for the replicate
    qst_result_norm[[paste0("replicate_", replicate)]] <- qst_resutl
  }
  
  # Store Qst results for the replication
  l_minor_replication[[paste0("replication_", number)]] <- qst_result_norm
}
```

### within replication
```{r}
# Define the output folder and create it if necessary
output_folder <- "./result/l/maf/within_replication_qqplot"
if (!dir.exists(output_folder)) {
  dir.create(output_folder, recursive = TRUE)  # Create folder if it doesn't exist
}

# Loci comparisons
loci_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Output files for statistical results
ks_test_file <- file.path(output_folder, "ks_test_results.txt")
ad_test_file <- file.path(output_folder, "ad_test_results.txt")
anova_file <- file.path(output_folder, "anova_results.txt")
ttest_file <- file.path(output_folder, "t_test_results.txt")

# Initialize file connections
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA and Tukey HSD Results\n")
cat("===========================\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("================\n\n")
sink()

# Loop over replications
for (replication_name in names(l_minor_replication)) {
  current_replication <- l_minor_replication[[replication_name]]  # Extract current replication
  
  # Initialize data for ANOVA and T-tests
  all_loci_values <- list()
  
  # Loop over loci comparisons
  for (comparison in loci_comparisons) {
    loci_x <- comparison[1]
    loci_y <- comparison[2]
    
    # Extract and combine data across all replicates for the loci sets
    combined_data <- do.call(rbind, lapply(names(current_replication), function(replicate_name) {
      replicate_data <- current_replication[[replicate_name]]
      data.frame(
        Replicate = replicate_name,
        x = replicate_data[[loci_x]],
        y = replicate_data[[loci_y]]
      )
    }))
    
    # Store data for ANOVA and T-tests
    all_loci_values[[loci_x]] <- combined_data$x
    all_loci_values[[loci_y]] <- combined_data$y
    
    # Perform KS Test
    ks_test <- ks.test(combined_data$x, combined_data$y)
    sink(ks_test_file, append = TRUE)
    cat("KS Test for", loci_x, "vs", loci_y, "in", replication_name, ":\n")
    print(ks_test)
    cat("\n")
    sink()
    
    # Perform AD Test
    if (length(combined_data$x) > 1 && length(combined_data$y) > 1) {
  ad_test <- kSamples::ad.test(combined_data$x, combined_data$y)
  sink(ad_test_file, append = TRUE)
  cat("AD Test for", loci_x, "vs", loci_y, "in", replication_name, ":\n")
  print(ad_test)
  cat("\n")
  sink()
} else {
  sink(ad_test_file, append = TRUE)
  cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "in", replication_name, "\n\n")
  sink()
}
    
    # Generate QQ plot
    x_sorted <- sort(combined_data$x, na.last = TRUE)
    y_sorted <- sort(combined_data$y, na.last = TRUE)
    plot_data <- data.frame(x = x_sorted, y = y_sorted)
    
    plot <- ggplot(data = plot_data, aes(x = y, y = x)) +
      geom_point(color = "blue") +
      geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
      labs(
        title = paste(loci_x, "vs", loci_y, "-", replication_name),
        x = paste(loci_y),
        y = paste(loci_x)
      ) +
      theme_minimal() +
      coord_fixed() +
      scale_x_continuous(limits = c(0.0, 0.1)) +
      scale_y_continuous(limits = c(0.0, 0.1))
    
    file_name <- file.path(output_folder, paste0("QQ_Plot_", loci_x, "_vs_", loci_y, "_", replication_name, ".png"))
    ggsave(filename = file_name, plot = plot, width = 6, height = 4)
  }
  
  # Combine data for ANOVA and T-tests
  loci_groups <- unlist(lapply(names(all_loci_values), function(loci) {
    rep(loci, length(all_loci_values[[loci]]))
  }))
  qst_values <- unlist(all_loci_values)
  data <- data.frame(
    LociGroup = factor(loci_groups, levels = names(all_loci_values)),
    QstValue = qst_values
  )
  
  # Perform ANOVA
  anova_results <- aov(QstValue ~ LociGroup, data = data)
  sink(anova_file, append = TRUE)
  cat("ANOVA Results for", replication_name, ":\n")
  print(summary(anova_results))
  cat("\n")
  
  # Tukey's HSD Post-Hoc Test
  cat("Tukey HSD Results for", replication_name, ":\n")
  tukey_results <- TukeyHSD(anova_results)
  print(tukey_results)
  cat("\n")
  sink()
  
  # Perform T-Test
  t_test_results <- pairwise.t.test(
    data$QstValue,
    data$LociGroup,
    p.adjust.method = "bonferroni"
  )
  sink(ttest_file, append = TRUE)
  cat("T-Test Results for", replication_name, ":\n")
  print(t_test_results)
  cat("\n")
  sink()
}
```


### between replication
```{r}
# Set output directory
output_dir <- "./result/l/maf/between_replication_qqplot/"
if (!dir.exists(output_dir)) dir.create(output_dir)

# Output files for statistical results
ks_test_file <- file.path(output_dir, "ks_test_results.txt")
ad_test_file <- file.path(output_dir, "ad_test_results.txt")
anova_file <- file.path(output_dir, "anova_results.txt")
ttest_file <- file.path(output_dir, "t_test_results.txt")

# Initialize file connections
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA Results\n")
cat("=============\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("==============\n\n")
sink()


# Assuming `replication` is the nested structure
data <- flatten_replication_data(l_minor_replication)

# Define loci comparisons
loci_comparisons <- list(
  c("N_1", "N_1"),
  c("N_10", "N_10"),
  c("N_100", "N_100"),
  c("N_1000", "N_1000"),
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Perform statistical comparisons and save results
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Filter data for the two loci
  data_x <- data %>% filter(Loci == loci_x) %>% pull(QstValue)
  data_y <- data %>% filter(Loci == loci_y) %>% pull(QstValue)
  
  # Perform KS Test
  if (length(data_x) > 1 && length(data_y) > 1) {
    ks_test <- ks.test(data_x, data_y)
    sink(ks_test_file, append = TRUE)
    cat("KS Test for", loci_x, "vs", loci_y, ":\n")
    print(ks_test)
    cat("\n")
    sink()
  }
  
  # Perform AD Test using kSamples
if (length(data_x) > 1 && length(data_y) > 1) {
  ad_test <- kSamples::ad.test(data_x, data_y)
  sink(ad_test_file, append = TRUE)
  cat("AD Test for", loci_x, "vs", loci_y, ":\n")
  print(ad_test)
  cat("\n")
  sink()
} else {
  sink(ad_test_file, append = TRUE)
  cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "\n\n")
  sink()
}
}

# Grouped data for ANOVA and T-Test
anova_data <- data %>%
  filter(Loci %in% unlist(loci_comparisons)) %>%
  group_by(Loci) %>%
  summarise(QstValues = list(QstValue), .groups = "drop") %>%
  unnest(cols = c(QstValues))

# Perform ANOVA
anova_results <- aov(QstValue ~ Loci, data = data)
sink(anova_file, append = TRUE)
cat("ANOVA Results:\n")
print(summary(anova_results))
cat("\n")
sink()

# Perform T-Test
t_test_results <- pairwise.t.test(
  data$QstValue,
  data$Loci,
  p.adjust.method = "bonferroni"
)
sink(ttest_file, append = TRUE)
cat("T-Test Results:\n")
print(t_test_results)
cat("\n")
sink()
# Define loci comparisons for QQ plots
qqplot_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Generate QQ plots for specified comparisons
for (comparison in qqplot_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Filter data for the two loci
  data_x <- data %>% filter(Loci == loci_x) %>% pull(QstValue)
  data_y <- data %>% filter(Loci == loci_y) %>% pull(QstValue)
  
  if (length(data_x) > 1 && length(data_y) > 1) {
    # Generate QQ plot
    qqplot_data <- data.frame(
      x = sort(data_x),
      y = sort(data_y)
    )
    
    qq_plot <- ggplot(qqplot_data, aes(x = x, y = y)) +
      geom_point(color = "blue") +
      geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
      labs(
        title = paste("QQ Plot:", loci_x, "vs", loci_y),
        x = paste(loci_x ),
        y = paste(loci_y)
      ) +
      theme_minimal() +
      coord_fixed()+
      scale_x_continuous(limits = c(0.0, 0.1)) +
      scale_y_continuous(limits = c(0.0, 0.1))
    
    # Save the QQ plot
    qqplot_file <- file.path(output_dir, paste0("QQ_Plot_", loci_x, "_vs_", loci_y, ".png"))
    ggsave(qqplot_file, qq_plot, width = 6, height = 6)
  } else {
    cat("Insufficient data for QQ Plot for", loci_x, "vs", loci_y, "\n")
  }
}
```


## average
```{r}
# Define loci comparisons
loci_comparisons <- list(
  c("N_1", "N_10"),
  c("N_1", "N_100"),
  c("N_1", "N_1000"),
  c("N_10", "N_100"),
  c("N_10", "N_1000"),
  c("N_100", "N_1000")
)

# Create an output folder
output_folder <- "./result/l/maf/average_qqplots"
if (!dir.exists(output_folder)) dir.create(output_folder)

# Output files for statistical results
ks_test_file <- file.path(output_folder, "ks_test_results.txt")
ad_test_file <- file.path(output_folder, "ad_test_results.txt")
anova_file <- file.path(output_folder, "anova_results.txt")
ttest_file <- file.path(output_folder, "t_test_results.txt")

# Initialize output files
sink(ks_test_file, append = FALSE)
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")
sink()

sink(ad_test_file, append = FALSE)
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")
sink()

sink(anova_file, append = FALSE)
cat("ANOVA and Tukey HSD Results\n")
cat("===========================\n\n")
sink()

sink(ttest_file, append = FALSE)
cat("T-Test Results\n")
cat("================\n\n")
sink()

# Loop over loci comparisons
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Average values over all replications for each replicate
  averaged_data <- do.call(rbind, lapply(names(l_minor_replication[[1]]), function(replicate_name) {
    # Extract replicate data across all replications
    replicate_values <- do.call(rbind, lapply(names(l_minor_replication), function(replication_name) {
      l_minor_replication[[replication_name]][[replicate_name]]
    }))
    
    # Ensure data is numeric
    numeric_values <- as.data.frame(lapply(as.data.frame(replicate_values), as.numeric))
    
    # Compute averages for loci_x and loci_y
    data.frame(
      Replicate = replicate_name,
      x = mean(numeric_values[[loci_x]], na.rm = TRUE),
      y = mean(numeric_values[[loci_y]], na.rm = TRUE)
    )
  }))
  
  # Sort values for quantile-quantile plotting
  x_sorted <- sort(averaged_data$x, na.last = TRUE)
  y_sorted <- sort(averaged_data$y, na.last = TRUE)
  
  # Perform Kolmogorov-Smirnov Test
  ks_test <- ks.test(x_sorted, y_sorted)
  sink(ks_test_file, append = TRUE)
  cat("KS Test for", loci_x, "vs", loci_y, ":\n")
  print(ks_test)
  cat("\n")
  sink()
  
  # Perform Anderson-Darling Test
  if (length(x_sorted) > 1 && length(y_sorted) > 1) {
  ad_test <- kSamples::ad.test(x_sorted, y_sorted)
  sink(ad_test_file, append = TRUE)
  cat("AD Test for", loci_x, "vs", loci_y, ":\n")
  print(ad_test)
  cat("\n")
  sink()
} else {
  sink(ad_test_file, append = TRUE)
  cat("Insufficient data for AD Test for", loci_x, "vs", loci_y, "\n\n")
  sink()
}
  
   # Combine data for ANOVA and t-tests
  combined_data <- data.frame(
    Group = rep(c(loci_x, loci_y), each = length(x_sorted)),
    Value = c(x_sorted, y_sorted)
  )
  
  # Perform ANOVA
  anova_results <- aov(Value ~ Group, data = combined_data)
  sink(anova_file, append = TRUE)
  cat("ANOVA Results for", loci_x, "vs", loci_y, ":\n")
  print(summary(anova_results))
  cat("\n")
  
  # Tukey's HSD Post-Hoc Test
  cat("Tukey HSD Results for", loci_x, "vs", loci_y, ":\n")
  tukey_results <- TukeyHSD(anova_results)
  print(tukey_results)
  cat("\n")
  sink()
  
  # Perform t-test
  t_test_results <- t.test(x_sorted, y_sorted)
  sink(ttest_file, append = TRUE)
  cat("T-Test Results for", loci_x, "vs", loci_y, ":\n")
  print(t_test_results)
  cat("\n")
  sink()
  
  # Create a data frame for plotting
  plot_data <- data.frame(x = x_sorted, y = y_sorted)
  
  # Generate QQ plot
  plot <- ggplot(data = plot_data, aes(x = y, y = x)) +
    geom_point(color = "blue") +
    geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
    labs(
      title = paste("Averaged QQ Plot:", loci_x, "vs", loci_y),
      x = paste( loci_y),
      y = paste( loci_x)
    ) +
    theme_minimal() +
    coord_fixed() +
    scale_x_continuous(limits = c(0.0, 0.1)) +
    scale_y_continuous(limits = c(0.0, 0.1))
  
  # Save the plot
  file_name <- file.path(output_folder, paste0("Averaged_QQ_Plot_", loci_x, "_vs_", loci_y, ".png"))
  ggsave(filename = file_name, plot = plot, width = 6, height = 4)
}

```



# FST
```{r}
transposed_num <- as.matrix(t(data_num[-1]))
str(transposed_num)
colnames(transposed_num) <- data_num$RowID      # Use RowID as column names
rownames(transposed_num) <- colnames(data_num)[-1]

# Create a vector of population identifiers
population_vector <- c(rep("pop1", 20), rep("pop2", 20), rep("pop3", 20), rep("pop4", 20), rep("pop5", 20), rep("pop6", 20), rep("pop7", 20), rep("pop8", 20) )

# Randomly sample one column
random_col <- sample(ncol(transposed_num), 1)  # Randomly select a column index
sampled_column <- transposed_num[, random_col] # Extract the column

wc_data <- data.frame(
  pop = population_vector,       # Population vector
  locus1 = sampled_column        # Sampled column data
)
fst <- wc(wc_data)

print(fst)
```