---
title: "R_analysis"
author: "Jikaël Ntoko"
date: "2024-11-19"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Library
Used : vcfR, dplyr, tidyr
``` {r}
if (!require("vcfR")) {
  install.packages("vcfR")
  library(vcfR)
}
if (!require("dplyr")) {
  install.packages("dplyr")
  library(dplyr)
}
if (!require("tidyr")) {
  install.packages("tidyr")
  library(tidyr)
}
library(kSamples)  # Required for ad.test
# Load required library for plotting
library(ggplot2)
library(hierfstat)

```
### Working directory, reproducibility
```{r}
set.seed(123) #Reproducibility
getwd()
```
###Custom methods
```{r}
# Qst function
calculate_qst <- function(pop_phenotypes) {
  pop_mean <- colMeans(pop_phenotypes)  # each col is a pop : mean of each population : result a vector
  overall_mean <- mean(pop_mean)     # mean of the resulting vector
  V_B <- mean((pop_mean - overall_mean)^2) #variance between population
  
  V_W <- mean(apply(pop_phenotypes, 2, var)) #compute the variance for each population (apply on column (2) since each column is a population) (diploid) and take the average
  
  # Calculate Qst
  Qst <- V_B / (V_B + 2 * V_W)
  return(Qst)
}
```
### Process directories
```{r}
data_directory <- "./Data/neutral/"

#list all directories
all_vcf <- list.files(path= data_directory, full.names = TRUE, pattern='\\.vcf$')
#all_vcf <- ("./Data/neutral/Seed_2035_all_pop.vcf")
```
### custom function
```{r}
# Function to convert genotypes to numeric values
convert_genotypes <- function(df) {
  # Safeguard for empty or corrupted data
  if (is.null(df) || nrow(df) == 0) {
    stop("Input data frame is empty or invalid!")
  }
  
  # Replace genotypes with numeric values
  df_numeric <- as.data.frame(apply(df, 2, function(col) {
    col <- gsub("0\\|0", "0", col)  # Replace "0|0" with "0"
    col <- gsub("1\\|0|0\\|1", "1", col)  # Replace "1|0" or "0|1" with "1"
    col <- gsub("1\\|1", "2", col)  # Replace "1|1" with "2"
    as.numeric(col)  # Convert to numeric, introduce NA for invalid values
  }))
  
  # Ensure the row names are correctly assigned
  if (nrow(df_numeric) == nrow(df)) {
    rownames(df_numeric) <- rownames(df)  # Assign row names
  } else {
    # Print diagnostic information for debugging
    cat("Mismatch detected!\n")
    cat("Original data frame dimensions:", nrow(df), ncol(df), "\n")
    cat("Numeric data frame dimensions:", nrow(df_numeric), ncol(df_numeric), "\n")
    stop("Mismatch between row names and number of rows in df_numeric!")
  }
  
  return(df_numeric)
}
```
## Load VCF file in r 
```{r}
replicate_no <- 1
data_numeric <- list()
# Number of repetitions for sampling
for (vcf in all_vcf){
  start.time <- Sys.time()
  print(paste0("processing :" ,vcf))
  
  data <- read.vcfR(vcf)
  #extract genotype
  genotype_inf <- extract.gt(data) 
  
  # Population range
  population_ranges <- list(
    pop1 = 1:20,   # i0 to i19
    pop2 = 21:40,  # i20 to i39
    pop3 = 41:60,  # i40 to i59
    pop4 = 61:80,  # i60 to i79
    pop5 = 81:100, # i80 to i99
    pop6 = 101:120,# i100 to i119
    pop7 = 121:140,# i120 to i139
    pop8 = 141:160 # i140 to i159
  )
  
  #split gt info into the 8 populations
  population_data <- lapply(names(population_ranges), function(pop_name) {
  # Extract columns corresponding to the population range
  cols <- population_ranges[[pop_name]]
  genotype_inf[, cols, drop = FALSE]
  })
  
  #assign names to the list for references purpose
  names(population_data) <- names(population_ranges)
  gc()
  #convert to numeric
  population_data_numeric <- lapply(population_data, convert_genotypes)

  data_numeric[[replicate_no]] <- population_data_numeric
  replicate_no <- replicate_no + 1
  
  end.time <- Sys.time()
  time.taken <- end.time - start.time
  print("___________")
  print(time.taken)
  print("___________")
}
### Write them into csv

output_folder <- "./Data/csv/"

# Ensure the output folder exists
if (!dir.exists(output_folder)) {
  dir.create(output_folder)
}

# Save each replication
for (replicate_no in seq_along(data_numeric)) {
  # Subfolder for this replication
  replicate_folder <- file.path(output_folder, paste0("replicate_", replicate_no))
  if (!dir.exists(replicate_folder)) {
    dir.create(replicate_folder)
  }
  
  # Access the population data for this replicate
  replicate_data <- data_numeric[[replicate_no]]
  
  # Save each population as a CSV
  for (pop_name in names(replicate_data)) {
    file_path <- file.path(replicate_folder, paste0(pop_name, ".csv"))
    write.csv(replicate_data[[pop_name]], file = file_path, row.names = FALSE)
  }
  
  # Print progress
  #print(paste0("Saved replicate ", replicate_no, " to ", replicate_folder))
}
```
##### Wo minor allele sampling norm distr effect size
Qst calc and store it in a df
```{r}
# Initialize the result list
sampling_norm_result <- list()

# Outer loop for iterations (1 to 10)
for (i in 1:10) {  # Corrected range to seq(1, 10) or 1:10
  num_replicates <- length(data_numeric) # Number of replicates
  loci_counts <- c(1, 10, 100, 1000)     # Number of loci to sample
  loci_columns <- paste0(loci_counts, "_loci")  # Column names for the final data frame
  
  # Create the result data frame for this iteration
  norm_result_df <- data.frame(matrix(ncol = length(loci_columns), nrow = num_replicates))
  colnames(norm_result_df) <- loci_columns
  rownames(norm_result_df) <- paste0("replicate_", seq_len(num_replicates))
  
  # Process each replicate
  for (replicate_no in seq_along(data_numeric)) {
    replicate_data <- data_numeric[[replicate_no]]  # Access the replicate data (list of 8 populations)
    
    for (loci in loci_counts) {
      # Randomly sample loci
      sampled_loci <- sample(nrow(replicate_data[[1]]), loci, replace = FALSE)
      
      # Generate random effect sizes
      effect_sizes <- rnorm(loci)  # Random normal distribution for effect sizes
      
      # Apply effect sizes and calculate phenotypes
      phenotypes <- lapply(replicate_data, function(pop_data) {
        sampled_data <- pop_data[sampled_loci, , drop = FALSE]
        colSums(sampled_data * effect_sizes)
      })
      
      # Combine phenotypes into a matrix (rows = individuals, columns = populations)
      phenotypes_matrix <- do.call(cbind, phenotypes)
      
      # Calculate Qst for this loci count
      Qst_value <- calculate_qst(phenotypes_matrix)
      
      # Assign the Qst value to the appropriate column in the result data frame
      norm_result_df[replicate_no, paste0(loci, "_loci")] <- Qst_value
    }
    
    # Print progress
    print(paste0("Processed replicate ", replicate_no, " for iteration ", i))
  }
  
  # Save the result data frame for this iteration
  sampling_norm_result[[i]] <- norm_result_df
}

# Inspect the result
#print(sampling_norm_result)

```
QQ plot
```{r}
# Create the output directory if it doesn't exist
output_dir <- "./result/norm_distrib_qqplot"
if (!dir.exists(output_dir)) {
  dir.create(output_dir, recursive = TRUE)
}

# Loci comparisons for QQ plots
loci_comparisons <- list(
  c("1_loci", "10_loci"),
  c("1_loci", "100_loci"),
  c("1_loci", "1000_loci"),
  c("10_loci", "100_loci"),
  c("10_loci", "1000_loci"),
  c("100_loci", "1000_loci"),
  c("1_loci", "1_loci"),
  c("10_loci", "10_loci"),
  c("100_loci", "100_loci"),
  c("1000_loci", "1000_loci")
)

# Create and save QQ plots for each iteration
for (i in seq_along(sampling_norm_result)) {
  norm_result_df <- sampling_norm_result[[i]]  # Data frame for this iteration
  
  # Iterate over each loci comparison
  for (comparison in loci_comparisons) {
    loci_x <- comparison[1]
    loci_y <- comparison[2]
    
    # Extract the Qst values for the two loci sets
    x_values <- norm_result_df[[loci_x]]
    y_values <- norm_result_df[[loci_y]]
    
    # Sort the values to compute quantiles
    x <- sort(x_values)
    y <- sort(y_values)
    
    # Create a data frame for plotting
    plot_data <- data.frame(x, y)
    
    # Create a custom QQ plot
    plot <- ggplot(data = plot_data, aes(x = y, y = x)) +
      geom_point(color = "blue") +
      geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
      labs(
        title = paste(loci_x, "vs", loci_y, "- Iteration", i),
        x = paste(loci_y),
        y = paste(loci_x)
      ) +
      theme_minimal() +
      coord_fixed() +
      scale_x_continuous(limits = c(0.0, 0.065)) +
      scale_y_continuous(limits = c(0.0, 0.065))
      
    # Define the file name and save the plot
    file_name <- file.path(output_dir, paste0("QQ_Plot_", loci_y, "_vs_", loci_x, "_Iteration_", i, ".png"))
    ggsave(filename = file_name, plot = plot, width = 6, height = 4)
  }
}


```

## All iteration per replicate
```{r}
# Create the output directory if it doesn't exist
output_dir <- "./result/norm_distrib_qqplot_all_data"
if (!dir.exists(output_dir)) {
  dir.create(output_dir, recursive = TRUE)
}

# Loci comparisons for QQ plots
loci_comparisons <- list(
  c("1_loci", "10_loci"),
  c("1_loci", "100_loci"),
  c("1_loci", "1000_loci"),
  c("10_loci", "100_loci"),
  c("10_loci", "1000_loci"),
  c("100_loci", "1000_loci")
)

# Initialize empty data frames for each loci comparison
comparison_data <- lapply(loci_comparisons, function(x) data.frame(x = numeric(0), y = numeric(0)))

# Iterate over all iterations in sampling_norm_result
for (i in seq_along(sampling_norm_result)) {
  norm_result_df <- sampling_norm_result[[i]]  # Data frame for this iteration
  
  # Combine all iterations into the respective loci comparison
  for (j in seq_along(loci_comparisons)) {
    loci_x <- loci_comparisons[[j]][1]
    loci_y <- loci_comparisons[[j]][2]
    
    # Extract and sort Qst values
    x_values <- sort(norm_result_df[[loci_x]])
    y_values <- sort(norm_result_df[[loci_y]])
    
    # Append quantiles to the comparison data
    comparison_data[[j]] <- rbind(comparison_data[[j]], data.frame(x = x_values, y = y_values))
  }
}

# Create and save a QQ plot for each loci comparison
for (j in seq_along(loci_comparisons)) {
  loci_x <- loci_comparisons[[j]][1]
  loci_y <- loci_comparisons[[j]][2]
  
  # Get the combined data for this comparison
  plot_data <- comparison_data[[j]]
  
  # Create a custom QQ plot
  plot <- ggplot(data = plot_data, aes(x = x, y = y)) +
    geom_point(color = "blue", alpha = 0.5) +
    geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
    labs(
      title = paste( loci_x, "vs", loci_y),
      x = paste(loci_x),
      y = paste(loci_y)
    ) +
    theme_minimal() +
    coord_fixed() +
    scale_x_continuous(limits = c(0.0, 0.065)) +
    scale_y_continuous(limits = c(0.0, 0.065))
  
  
  # Define the file name and save the plot
  file_name <- file.path(output_dir, paste0("QQ_Plot_", loci_y, "_vs_", loci_x, "_All_Data.png"))
  ggsave(filename = file_name, plot = plot, width = 8, height = 6)
}
```

Plot the average over 10 iteration
```{r}
# Create the output directory if it doesn't exist
output_dir <- "./result/norm_distrib_avg_qqplot"
if (!dir.exists(output_dir)) {
  dir.create(output_dir, recursive = TRUE)
}

# Loci comparisons for QQ plots
loci_comparisons <- list(
  c("1_loci", "10_loci"),
  c("1_loci", "100_loci"),
  c("1_loci", "1000_loci"),
  c("10_loci", "100_loci"),
  c("10_loci", "1000_loci"),
  c("100_loci", "1000_loci"),
  c("1_loci", "1_loci"),
  c("10_loci", "10_loci"),
  c("100_loci", "100_loci"),
  c("1000_loci", "1000_loci")
)

# Combine all iterations into one data frame for each loci
combined_qst <- lapply(names(sampling_norm_result[[1]]), function(loci) {
  do.call(cbind, lapply(sampling_norm_result, function(df) df[[loci]]))
})
names(combined_qst) <- names(sampling_norm_result[[1]])

# Compute the per-replicate averages across 10 iterations
average_per_loci <- lapply(combined_qst, function(matrix) {
  rowMeans(matrix, na.rm = TRUE)
})

# Generate QQ plots for each loci comparison
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Extract the averaged Qst values for the two loci sets
  x_values <- average_per_loci[[loci_x]]
  y_values <- average_per_loci[[loci_y]]
  
  # Create a data frame for plotting
  plot_data <- data.frame(x_values = sort(x_values), y_values = sort(y_values))
  
  # Debug: Print plot data
  print("Plot Data:")
  print(plot_data)
  
  # Create the QQ plot
  plot <- ggplot(data = plot_data, aes(x = y_values, y = x_values)) +
    geom_point(color = "blue") +
    geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
    labs(
      title = paste("Average Qst value :", loci_x, "vs", loci_y),
      x = paste( loci_y),
      y = paste( loci_x)
    ) +
    theme_minimal() +
    coord_fixed() +
    scale_x_continuous(limits = c(0.0, 0.065)) +
    scale_y_continuous(limits = c(0.0, 0.065))
  
  # Define the file name and save the plot
  file_name <- file.path(output_dir, paste0("QQ_Plot_", loci_x, "_vs_", loci_y, "_avg.png"))
  ggsave(filename = file_name, plot = plot, width = 6, height = 4)
}


```

Statistical test

The null hypothesis for the Kolmogorov-Smirnov (KS) test is:

The two samples come from the same continuous distribution.

if we get p_value > 0.05 : the distributions are not significantly different.
```{r}
# Perform KS test for each loci comparison
ks_test_results <- list()
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  x_values <- average_per_loci[[loci_x]]
  y_values <- average_per_loci[[loci_y]]
  
  # Perform KS test
  ks_test <- ks.test(x_values, y_values)
  
  # Store the results
  ks_test_results[[paste(loci_x, loci_y, sep = " vs ")]] <- ks_test
}

# Specify the output file
output_file <- "./result/norm_distrib_avg_qqplot/ks_test_results.txt"

# Open the file connection
sink(output_file)

# Write the KS test results
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")


# Print the KS test results
for (comparison in names(ks_test_results)) {
  cat("KS Test for", comparison, ":\n")
  print(ks_test_results[[comparison]])
  cat("\n")
}
# Close the file connection
sink()

# Perform Anderson-Darling test for each loci comparison
ad_test_results <- list()
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  x_values <- average_per_loci[[loci_x]]
  y_values <- average_per_loci[[loci_y]]
  
  # Perform Anderson-Darling test
  ad_test <- ad.test(x_values, y_values)
  
  ad_test_results[[paste(loci_x, loci_y, sep = " vs ")]] <- ad_test
}

# Specify the output file
output_file <- "./result/norm_distrib_avg_qqplot/ad_test_results.txt"

# Open the file connection
sink(output_file)

# Write the Anderson-Darling test results
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")

# Print the Anderson-Darling test results
for (comparison in names(ad_test_results)) {
  cat("Anderson-Darling Test for", comparison, ":\n")
  print(ad_test_results[[comparison]])
  cat("\n")
}

# Close the file connection
sink()
 
```
Anova and t-test
```{r}
# Combine Qst values into a single data frame
loci_groups <- unlist(lapply(names(average_per_loci), function(loci) {
  rep(loci, length(average_per_loci[[loci]]))
}))
qst_values <- unlist(average_per_loci)

# Create a data frame for analysis
data <- data.frame(
  LociGroup = factor(loci_groups, levels = names(average_per_loci)),
  QstValue = qst_values
)

# Perform ANOVA
anova_results <- aov(QstValue ~ LociGroup, data = data)

# Specify the output file
output_file_anova <- "./result/norm_distrib_avg_qqplot/anova_results.txt"

# Save the ANOVA results
sink(output_file_anova)
cat("ANOVA Results\n")
cat("=============\n\n")
print(summary(anova_results))
cat("\n")

# Perform Tukey's HSD post-hoc test
cat("Tukey HSD Post-hoc Test\n")
cat("========================\n\n")
tukey_results <- TukeyHSD(anova_results)
print(tukey_results)
sink()

## ttest

# Perform pairwise t-tests with Bonferroni correction
t_test_results <- pairwise.t.test(
  data$QstValue,
  data$LociGroup,
  p.adjust.method = "bonferroni"
)

# Specify the output file
output_file_ttest <- "./result/norm_distrib_avg_qqplot/t_test_results.txt"

# Save the t-test results
sink(output_file_ttest)
cat("Pairwise T-Test Results\n")
cat("========================\n\n")
print(t_test_results)
sink()


```
##### With minor allele sampling norm distr effect size
### on the meta pop !

```{r}
maf_threshold <- 0.05

filtered_data_numeric <- list()  # To store filtered data for all replicates

for (replicate_no in seq_along(data_numeric)) {
  print(paste0("Processing replicate : ", replicate_no))
  replicate_data <- data_numeric[[replicate_no]]  # Access data for this replicate
  
  # Combine the populations column-wise
  combined_data <- do.call(cbind, replicate_data)
  
  # Calculate MAF for each locus across all populations
  meta_maf <- apply(combined_data, 1, function(row) {
    n_individuals <- length(row)
    count_0 <- sum(row == 0)
    count_1 <- sum(row == 1)
    count_2 <- sum(row == 2)
    freq_A <- (count_0 * 2 + count_1) / (2 * n_individuals)
    freq_B <- 1 - freq_A
    return(min(freq_A, freq_B))  # Return MAF
  })
  
  # Identify loci to keep based on the MAF threshold
  loci_to_keep <- which(meta_maf > maf_threshold)
  
  # Filter the combined data
  filtered_combined_data <- combined_data[loci_to_keep, , drop = FALSE]
  
  # Split the filtered data back into 8 populations
  filtered_replicate_data <- list()
  for (pop_name in names(population_ranges)) {
    cols <- population_ranges[[pop_name]]  # Columns corresponding to this population
    filtered_replicate_data[[pop_name]] <- filtered_combined_data[, cols, drop = FALSE]
  }
  
  # Store the filtered replicate data
  filtered_data_numeric[[replicate_no]] <- filtered_replicate_data
}


```
```{r}
print(dim(filtered_combined_data))
print(sapply(filtered_replicate_data, dim))
```

Caluclate Qst
```{r}
# Initialize the result list
sampling_norm_minor_res <- list()

# Outer loop for iterations (1 to 10)
for (i in 1:10) {
  num_replicates <- length(filtered_data_numeric)  # Number of replicates
  loci_counts <- c(1, 10, 100, 1000)      # Number of loci to sample
  loci_columns <- paste0(loci_counts, "_loci")  # Column names for the final data frame
  
  # Create the result data frame for this iteration
  norm_result_df <- data.frame(matrix(ncol = length(loci_columns), nrow = num_replicates))
  colnames(norm_result_df) <- loci_columns
  rownames(norm_result_df) <- paste0("replicate_", seq_len(num_replicates))
  
  # Process each replicate
  for (replicate_no in seq_along(filtered_data_numeric)) {
    replicate_data <- filtered_data_numeric[[replicate_no]]  # Access the replicate data (list of 8 populations)
    
    for (loci in loci_counts) {
      # Randomly sample loci
      sampled_loci <- sample(nrow(replicate_data[[1]]), loci, replace = FALSE)
      
      # Generate random effect sizes
      effect_sizes <- rnorm(loci)  # Random normal distribution for effect sizes
      
      # Apply effect sizes and calculate phenotypes
      phenotypes <- lapply(replicate_data, function(pop_data) {
        sampled_data <- pop_data[sampled_loci, , drop = FALSE]
        colSums(sampled_data * effect_sizes)
      })
      
      # Combine phenotypes into a matrix (rows = individuals, columns = populations)
      phenotypes_matrix <- do.call(cbind, phenotypes)
      
      # Calculate Qst for this loci count
      Qst_value <- calculate_qst(phenotypes_matrix)
      
      # Assign the Qst value to the appropriate column in the result data frame
      norm_result_df[replicate_no, paste0(loci, "_loci")] <- Qst_value
    }
    
    # Print progress
    print(paste0("Processed replicate ", replicate_no, " for iteration ", i))
  }
  
  # Save the result data frame for this iteration
  sampling_norm_minor_res[[i]] <- norm_result_df
}

# Inspect the result
#print(sampling_norm_minor_res[[1]])

```
QQ plot each iteration
```{r}
# Create the output directory if it doesn't exist
output_dir <- "./result/norm_distrib_qqplot_minor"
if (!dir.exists(output_dir)) {
  dir.create(output_dir, recursive = TRUE)
}

# Loci comparisons for QQ plots
loci_comparisons <- list(
  c("1_loci", "10_loci"),
  c("1_loci", "100_loci"),
  c("1_loci", "1000_loci"),
  c("10_loci", "100_loci"),
  c("10_loci", "1000_loci"),
  c("100_loci", "1000_loci"),
  c("1_loci", "1_loci"),
  c("10_loci", "10_loci"),
  c("100_loci", "100_loci"),
  c("1000_loci", "1000_loci")
)

# Create and save QQ plots for each iteration
for (i in seq_along(sampling_norm_minor_res)) {
  norm_result_df <- sampling_norm_minor_res[[i]]  # Data frame for this iteration
  
  for (comparison in loci_comparisons) {
    loci_x <- comparison[1]
    loci_y <- comparison[2]
    
    x_values <- norm_result_df[[loci_x]]
    y_values <- norm_result_df[[loci_y]]
    
    x <- sort(x_values)
    y <- sort(y_values)
    
    plot_data <- data.frame(x, y)
    
    plot <- ggplot(data = plot_data, aes(x = y, y = x)) +
      geom_point(color = "blue") +
      geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
      labs(
        title = paste("", loci_y, "vs", loci_x, "- Iteration", i),
        x = paste("N_loci", loci_y),
        y = paste("N_loci", loci_x)
      ) +
      theme_minimal() +
      coord_fixed() +
      scale_x_continuous(limits = c(0.01, 0.035)) +
      scale_y_continuous(limits = c(0.01, 0.035))
    
    file_name <- file.path(output_dir, paste0("QQ_Plot_", loci_y, "_vs_", loci_x, "_Iteration_", i, ".png"))
    ggsave(filename = file_name, plot = plot, width = 6, height = 4)
  }
}

```
Average over 10 iteration
```{r}
# Create the output directory if it doesn't exist
output_dir <- "./result/norm_distrib_avg_qqplot_minor"
if (!dir.exists(output_dir)) {
  dir.create(output_dir, recursive = TRUE)
}

# Loci comparisons for QQ plots
loci_comparisons <- list(
  c("1_loci", "10_loci"),
  c("1_loci", "100_loci"),
  c("1_loci", "1000_loci"),
  c("10_loci", "100_loci"),
  c("10_loci", "1000_loci"),
  c("100_loci", "1000_loci"),
  c("1_loci", "1_loci"),
  c("10_loci", "10_loci"),
  c("100_loci", "100_loci"),
  c("1000_loci", "1000_loci")
)

# Combine all iterations into one data frame for each loci
combined_qst <- lapply(names(sampling_norm_minor_res[[1]]), function(loci) {
  do.call(cbind, lapply(sampling_norm_minor_res, function(df) df[[loci]]))
})
names(combined_qst) <- names(sampling_norm_minor_res[[1]])

# Compute the per-replicate averages across 10 iterations
average_per_loci <- lapply(combined_qst, function(matrix) {
  rowMeans(matrix, na.rm = TRUE)
})

# Generate QQ plots for each loci comparison
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  x_values <- average_per_loci[[loci_x]]
  y_values <- average_per_loci[[loci_y]]
  
  plot_data <- data.frame(x_values = sort(x_values), y_values = sort(y_values))
  
  plot <- ggplot(data = plot_data, aes(x = y_values, y = x_values)) +
    geom_point(color = "blue") +
    geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
    labs(
      title = paste("Average Qst value: ", loci_y, "vs", loci_x),
      x = paste("N_loci: ", loci_y),
      y = paste("N_loci: ", loci_x)
    ) +
    theme_minimal() +
    coord_fixed() +
    scale_x_continuous(limits = c(0.01, 0.035)) +
    scale_y_continuous(limits = c(0.01, 0.035))
  
  file_name <- file.path(output_dir, paste0("QQ_Plot_", loci_x, "_vs_", loci_y, "_avg.png"))
  ggsave(filename = file_name, plot = plot, width = 6, height = 6)
}

```
Statistical test
```{r}
# Perform KS test for each loci comparison
ks_test_results <- list()
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  x_values <- average_per_loci[[loci_x]]
  y_values <- average_per_loci[[loci_y]]
  
  ks_test <- ks.test(y_values, x_values)
  
  ks_test_results[[paste(loci_x, loci_y, sep = " vs ")]] <- ks_test
}

# Specify the output file
output_file <- "./result/norm_distrib_avg_qqplot_minor/ks_test_results.txt"

# Open the file connection
sink(output_file)

# Write the KS test results
cat("Kolmogorov-Smirnov Test Results\n")
cat("===============================\n\n")


# Print the KS test results
for (comparison in names(ks_test_results)) {
  cat("KS Test for", comparison, ":\n")
  print(ks_test_results[[comparison]])
  cat("\n")
}
# Close the file connection
sink()

```
Since the distribution between 10 and 100 seems to be significantly different. We test if their median are significantly different with a wilcox_test
```{r}
wilcox_test <- wilcox.test(average_per_loci[['100_loci']], average_per_loci[['1000_loci']])
wilcox_test


```

Test : Anderson-Darling ( same as previous but more sensitive to difference in the tail)
```{r}

# Perform Anderson-Darling test for each loci comparison
ad_test_results <- list()
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  x_values <- average_per_loci[[loci_x]]
  y_values <- average_per_loci[[loci_y]]
  
  # Perform Anderson-Darling test
  ad_test <- ad.test(x_values, y_values)
  
  ad_test_results[[paste(loci_x, loci_y, sep = " vs ")]] <- ad_test
}

# Specify the output file
output_file <- "./result/norm_distrib_avg_qqplot_minor/ad_test_results.txt"

# Open the file connection
sink(output_file)

# Write the Anderson-Darling test results
cat("Anderson-Darling Test Results\n")
cat("===============================\n\n")

# Print the Anderson-Darling test results
for (comparison in names(ad_test_results)) {
  cat("Anderson-Darling Test for", comparison, ":\n")
  print(ad_test_results[[comparison]])
  cat("\n")
}

# Close the file connection
sink()
```
Significant differences between 1 and 10 loci.
Ks test flagged additional difference for 10 vs 100 loci
let's visualize them
```{r}
# Combine Qst values into a data frame for plotting
plot_data <- data.frame(
  value = c(average_per_loci[["1_loci"]], average_per_loci[["10_loci"]], average_per_loci[["100_loci"]]),
  loci = rep(c("1_loci", "10_loci", "100_loci"), each = length(average_per_loci[["1_loci"]]))
)

# Plot density distributions
density_plot <- ggplot(plot_data, aes(x = value, fill = loci)) +
  geom_density(alpha = 0.5) +
  theme_minimal() +
  labs(
    title = "Density Plot of Qst Values",
    x = "Qst Value",
    y = "Density"
  ) +
  scale_fill_manual(values = c("1000_loci" = "blue", "10_loci" = "green", "100_loci" = "red")) +
  theme(legend.title = element_blank())

output_file <- "./result/norm_distrib_avg_qqplot_minor/density_plot_qst_values.png"
ggsave(filename = output_file, plot = density_plot, width = 8, height = 6)
```
Lets perform a wilcoxon rank-sum test to compare the medians of independent distribution.
```{r}
# Perform pairwise Wilcoxon rank-sum tests
wilcoxon_results <- list()

# Define the pairwise comparisons
loci_comparisons <- list(
  c("1_loci", "10_loci"),
  c("1_loci", "100_loci"),
  c("1_loci", "1000_loci"),
  c("10_loci", "100_loci"),
  c("10_loci", "1000_loci"),
  c("100_loci", "1000_loci"),
  c("1_loci", "1_loci"),
  c("10_loci", "10_loci"),
  c("100_loci", "100_loci"),
  c("1000_loci", "1000_loci")
)

# Loop through each pair and apply the Wilcoxon test
for (comparison in loci_comparisons) {
  loci_x <- comparison[1]
  loci_y <- comparison[2]
  
  # Extract Qst values
  x_values <- average_per_loci[[loci_x]]
  y_values <- average_per_loci[[loci_y]]
  
  # Perform the Wilcoxon rank-sum test
  test_result <- wilcox.test(x_values, y_values)
  
  # Store the results
  wilcoxon_results[[paste(loci_x, loci_y, sep = " vs ")]] <- test_result
}

output_file <- "./result/norm_distrib_avg_qqplot_minor/wilcoxon_test_results.txt"

# Open the file connection
sink(output_file)

# Write the Wilcoxon test results
cat("Wilcoxon Rank-Sum Test Results\n")
cat("===============================\n\n")

# Print the results
for (comparison in names(wilcoxon_results)) {
  cat("Wilcoxon Test for", comparison, ":\n")
  print(wilcoxon_results[[comparison]])
  cat("\n")
}

sink()

```
## Summary of Results

| **Comparison**        | **KS Test \( p \)-Value** | **Wilcoxon Test \( p \)-Value** | **AD Test \( p \)-Value** | **Conclusion**                       |
|------------------------|--------------------------|----------------------------------|--------------------------|---------------------------------------|
| **1_loci vs 10_loci**  | 0.01581 (Significant)   | 0.1899 (Not Significant)        | 0.016713 (Significant)   | Mixed results; likely some differences. |
| **1_loci vs 100_loci** | 0.8127 (Not Significant)| 0.8652 (Not Significant)        | 0.38331 (Not Significant)| No significant difference.            |
| **1_loci vs 1000_loci**| 0.4676 (Not Significant)| -                               | 0.13940 (Not Significant)| No significant difference.            |
| **10_loci vs 100_loci**| 0.01581 (Significant)   | 0.2544 (Not Significant)        | 0.15098 (Not Significant)| Mixed results; possible small differences. |
| **10_loci vs 1000_loci**| 0.3667 (Not Significant)| -                               | 0.58041 (Not Significant)| No significant difference.            |
| **100_loci vs 1000_loci**| 0.8127 (Not Significant)| -                               | 0.88632 (Not Significant)| No significant difference.            |

---

Conclusion:
1. **1 vs 10**: Mixed result. No significant result in median but significant result in distribution. May indicate distribution in shape rater than the tendency
2. **1 vs 100** : All test show no significance. Distribution likely similare in shape and tendency
3. **10 vs 100** : 
```{r}
# Combine Qst values into a single data frame
loci_groups <- unlist(lapply(names(average_per_loci), function(loci) {
  rep(loci, length(average_per_loci[[loci]]))
}))
qst_values <- unlist(average_per_loci)

# Create a data frame for analysis
data <- data.frame(
  LociGroup = factor(loci_groups, levels = names(average_per_loci)),
  QstValue = qst_values
)

# Perform ANOVA
anova_results <- aov(QstValue ~ LociGroup, data = data)

# Specify the output file
output_file_anova <- "./result/norm_distrib_avg_qqplot_minor/anova_results.txt"

# Save the ANOVA results
sink(output_file_anova)
cat("ANOVA Results\n")
cat("=============\n\n")
print(summary(anova_results))
cat("\n")

# Perform Tukey's HSD post-hoc test
cat("Tukey HSD Post-hoc Test\n")
cat("========================\n\n")
tukey_results <- TukeyHSD(anova_results)
print(tukey_results)
sink()

## ttest

# Perform pairwise t-tests with Bonferroni correction
t_test_results <- pairwise.t.test(
  data$QstValue,
  data$LociGroup,
  p.adjust.method = "bonferroni"
)

# Specify the output file
output_file_ttest <- "./result/norm_distrib_avg_qqplot_minor/t_test_results.txt"

# Save the t-test results
sink(output_file_ttest)
cat("Pairwise T-Test Results\n")
cat("========================\n\n")
print(t_test_results)
sink()
```
