---
title: "R_analysis"
author: "Jikaël Ntoko"
date: "2024-11-19"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Library
Used : vcfR, dplyr, tidyr
``` {r}
if (!require("vcfR")) {
  install.packages("vcfR")
  library(vcfR)
}
if (!require("dplyr")) {
  install.packages("dplyr")
  library(dplyr)
}
if (!require("tidyr")) {
  install.packages("tidyr")
  library(tidyr)
}
```
### Working directory, reproducibility
```{r}
set.seed(123) #Reproducibility
setwd("C:/Users/User/Desktop/Master project/R_analysis")
```
###Custom methods
```{r}
### Convert str genotype to numeric genotype
convert_genotype <- function(genotype) {
  alleles <- strsplit(genotype, "\\|")
  alleles <- lapply(alleles, as.numeric)
  return(sum(unlist(alleles)))
}

### Sample loci
sample_loci <- function(data, n_values) {
  data %>%
    group_by(Indiv) %>%
    summarise(
      samples = list(lapply(n_values, function(n) sample(gt_numeric, size = min(n, n()), replace = FALSE)))
    ) %>%
    unnest_wider(samples, names_sep = "_") %>%
    pivot_longer(
      cols = starts_with("samples_"),
      names_to = "Sample_Size",
      values_to = "gt_numeric_values"
    ) %>%
    unnest(gt_numeric_values)
}
```
### Process directories
```{r}
main_directory <- "./data/neutral/"

#list all directories
all_directories <- list.dirs(path= main_directory, full.names = TRUE)
```
### Processing vcf files and saving them by replicate
Process all vcf files, transform info into long-table and store them into a list classed by replicate
```{r}
all_data_list <- list()
for (directory in all_directories){
  if (directory != main_directory){
  files <- list.files(path = directory, pattern = "\\.vcf", full.names = T)
  data_list <- list()
  for (file in files) {
    data <- vcfR2tidy(read.vcfR(file))
    data_list[[basename(file)]] <- data
  
  }
  all_data_list[[basename(directory)]] <- data_list
  }
}
```
Transform the data into dataframe
```{r}
# Initialize the final list to store data by replicate
final_population_list <- list()

# Loop through each replicate in all_data_list
for (replicate_name in names(all_data_list)) {
  replicate_data <- all_data_list[[replicate_name]]  # Access replicate
  
  # Initialize a list to store data frames for each population (file) in this replicate
  population_data <- list()
  
  # Loop through each file in the replicate
  for (file_name in names(replicate_data)) {
    file_data <- replicate_data[[file_name]]  # Access file data
    
    # Extract `gt` data
    gt_data <- file_data$gt  # Access the gt list containing genotype data
    
    # Pivot data manually to create a wide-format data frame
    # Rows are positions (POS), columns are individuals (Indiv)
    gt_wide <- data.frame(POS = unique(gt_data$POS))
    
    # Loop through each individual and add their genotype (gt_GT) as a column
    for (indiv in unique(gt_data$Indiv)) {
      # Filter rows for the current individual
      indiv_data <- gt_data[gt_data$Indiv == indiv, ]
      
      # Add a new column for the individual's data
      gt_wide[[indiv]] <- indiv_data[match(gt_wide$POS, indiv_data$POS), "gt_GT"]
    }
    
    # Store the wide data frame for this population (file)
    population_data[[file_name]] <- gt_wide
  }
  
  # Store the population data for this replicate
  final_population_list[[replicate_name]] <- population_data
}

```

For each replicate find the common loci
```{r}
common_loci_list <- list()

for (replicate_name in names(all_data_list)) {
  data_list <- all_data_list[[replicate_name]]  # Access populations (files) in the replicate
  
  # Extract loci (POS) from each population
  loci_list <- lapply(data_list, function(data) unique(data$gt$POS))
  
  # Find common loci across all populations in the replicate
  common_loci <- Reduce(intersect, loci_list)  # Intersection of all loci
  
  # Store the common loci for this replicate
  common_loci_list[[replicate_name]] <- common_loci
}

# Inspect the results
str(common_loci_list)

```
Get all the genomic data with common loci for all the 8 populations in all the replicate
```{r}
# Initialize a list to store filtered and numeric data by replicate
genomic_numeric_data_list <- list()

# Loop through each replicate
for (replicate in seq_along(all_data_list)) {
  # Access the data list for the current replicate
  data_list <- all_data_list[[replicate]]
  common_loci <- common_loci_list[[replicate]]  # Common loci for this replicate
  
  # Initialize a list to store data for each population (file) in the replicate
  replicate_numeric_data <- list()
  
  # Process each file in the replicate
  for (file_name in names(data_list)) {
    # Access the genomic data for the current file
    file_data <- data_list[[file_name]]$gt
    
    # Filter data based on common loci
    filtered_data <- file_data[file_data$POS %in% common_loci, ]
    
    # Check if filtered data is non-empty
    if (nrow(filtered_data) > 0) {
      # Convert `gt_GT` to numeric using the provided `convert_genotype` function
      filtered_data$gt_numeric <- sapply(filtered_data$gt_GT, convert_genotype)
      
      # Add filtered data with numeric genotype to the list
      replicate_numeric_data[[file_name]] <- filtered_data
    } else {
      print(paste("No matching loci for file:", file_name))
    }
  }
  
  # Store the processed data for this replicate
  genomic_numeric_data_list[[paste("replicate", replicate, sep = "_")]] <- replicate_numeric_data
}

```
Add effect size
```{r}
# Parameters for effect size distribution
effect_mean <- 0  # Mean of the normal distribution
effect_sd <- 1    # Standard deviation of the normal distribution

# Initialize a list to store processed data by replicate
genomic_effect_data_list <- list()

# Loop through each replicate
for (replicate in seq_along(all_data_list)) {
  # Access the data list for the current replicate
  data_list <- all_data_list[[replicate]]
  common_loci <- common_loci_list[[replicate]]  # Common loci for this replicate
  
  # Initialize a list to store data for each population (file) in the replicate
  replicate_effect_data <- list()
  
  # Process each file in the replicate
  for (file_name in names(data_list)) {
    # Access the genomic data for the current file
    file_data <- data_list[[file_name]]$gt
    
    # Filter data based on common loci
    filtered_data <- file_data[file_data$POS %in% common_loci, ]
    
    # Check if filtered data is non-empty
    if (nrow(filtered_data) > 0) {
      # Convert `gt_GT` to numeric using the provided `convert_genotype` function
      filtered_data$gt_numeric <- sapply(filtered_data$gt_GT, convert_genotype)
      
      # Add an `effect_size` column drawn from a normal distribution
      filtered_data$effect_size <- rnorm(
        nrow(filtered_data), 
        mean = effect_mean, 
        sd = effect_sd
      )
      
      # Compute the phenotype (gt_numeric * effect_size)
      filtered_data$phenotype <- filtered_data$gt_numeric * filtered_data$effect_size
      
      # Add the processed data to the replicate list
      replicate_effect_data[[file_name]] <- filtered_data
    } else {
      print(paste("No matching loci for file:", file_name))
    }
  }
  
  # Store the processed data for this replicate
  genomic_effect_data_list[[paste("replicate", replicate, sep = "_")]] <- replicate_effect_data
}


```

Extract 1000, 100, 10, 1 loci for each replicate (10 times)
```{r}
# Parameters
sample_sizes <- c(1, 10, 100, 1000)  # Sample sizes
num_replicates <- 10  # Number of replications

# Initialize a list to store individual-level phenotype results
individual_phenotype_results <- list()

# Perform 10 replications
for (replication in seq_len(num_replicates)) {
  # Initialize a list to store results for this replication
  replication_results <- list()
  
  # Loop through each replicate
  for (replicate_name in names(genomic_effect_data_list)) {
    # Access the populations (files) for this replicate
    replicate_data <- genomic_effect_data_list[[replicate_name]]
    
    # Get all unique positions (POS) for the replicate (common across all populations)
    all_positions <- unique(do.call(rbind, lapply(replicate_data, function(file_data) file_data$POS)))
    
    # Initialize a list to store individual phenotypes for each sample size
    sample_results <- list()
    
    # Loop through each sample size
    for (sample_size in sample_sizes) {
      # Sample positions
      sampled_positions <- sample(all_positions, size = min(sample_size, length(all_positions)), replace = FALSE)
      
      # Initialize a list to store phenotypes for each population
      population_results <- list()
      
      # Loop through each population
      for (file_name in names(replicate_data)) {
        file_data <- replicate_data[[file_name]]
        
        # Filter the file data for the sampled positions
        sampled_data <- file_data[file_data$POS %in% sampled_positions, ]
        
        # Calculate the phenotype for each individual
        individual_phenotypes <- sampled_data[, c("Indiv", "phenotype"), drop = FALSE]
        
        # Store the individual-level phenotypes
        population_results[[file_name]] <- individual_phenotypes
      }
      
      # Store the population-level results for this sample size
      sample_results[[paste("sample", sample_size, sep = "_")]] <- population_results
    }
    
    # Store the results for this replicate
    replication_results[[replicate_name]] <- sample_results
  }
  
  # Store the results for this replication
  individual_phenotype_results[[paste("replication", replication, sep = "_")]] <- replication_results
}



```
### QST calculation
based on Qst = between-populations variance / (between population variance + 2 (diploid) * within-population variance (average across populations))
```{r}
# Initialize lists to store Qst results for each sample size
qst_sample_results <- list(
  sample_1 = list(),
  sample_10 = list(),
  sample_100 = list(),
  sample_1000 = list()
)

# Loop through each replication
for (replication_name in names(individual_phenotype_results)) {
  replication_data <- individual_phenotype_results[[replication_name]]  # Access replication data
  
  # Loop through each replicate
  for (replicate_name in names(replication_data)) {
    replicate_data <- replication_data[[replicate_name]]  # Access replicate data
    
    # Loop through each sample size
    for (sample_size in names(replicate_data)) {
      sample_data <- replicate_data[[sample_size]]  # Access sample data
      
      # Combine individual-level phenotypes across populations
      all_population_data <- do.call(rbind, lapply(sample_data, function(population_data) {
        population_data  # Data frame with Indiv and phenotype columns
      }))
      
      # Add population identifiers to the combined data
      all_population_data$population <- rep(names(sample_data), 
                                            sapply(sample_data, nrow))
      
      # Calculate between-population variance (Var_B)
      population_means <- aggregate(phenotype ~ population, data = all_population_data, FUN = mean)
      var_b <- var(population_means$phenotype, na.rm = TRUE)
      
      # Calculate within-population variance (Var_W)
      var_w <- mean(unlist(lapply(split(all_population_data, all_population_data$population), function(pop_data) {
        var(pop_data$phenotype, na.rm = TRUE)
      })))
      
      # Calculate Qst
      if (!is.na(var_b) && !is.na(var_w) && !(var_b == 0 && var_w == 0)) {
        qst <- var_b / (var_b + 2 * var_w)
      } else {
        qst <- NA  # Invalid variance values
      }
      
      # Store Qst in the appropriate sample size list
      qst_sample_results[[sample_size]][[replication_name]][[replicate_name]] <- qst
    }
  }
}

```

#### Visualization part
First: boxplot of Qst across all replicate by sample size for each replication we did
```{r}
library(ggplot2)

# Combine Qst results into a single data frame for plotting
plot_data <- data.frame(
  Sample = character(),
  Replication = character(),
  Qst = numeric(),
  stringsAsFactors = FALSE
)

# Loop through each sample size
for (sample_size in names(qst_sample_results)) {
  sample_data <- qst_sample_results[[sample_size]]
  
  # Loop through each replication
  for (replication_name in names(sample_data)) {
    replication_data <- sample_data[[replication_name]]
    
    # Combine replicate Qst values
    for (replicate_name in names(replication_data)) {
      qst_value <- replication_data[[replicate_name]]
      
      # Append to plot_data
      plot_data <- rbind(
        plot_data,
        data.frame(
          Sample = sample_size,
          Replication = replication_name,
          Qst = qst_value
        )
      )
    }
  }
}

# Ensure Sample is treated as a factor
plot_data$Sample <- factor(plot_data$Sample, levels = c("sample_1", "sample_10", "sample_100", "sample_1000"))

# Create the boxplot
ggplot(plot_data, aes(x = Sample, y = Qst, fill = Sample)) +
  geom_boxplot() +
  facet_wrap(~ Replication, ncol = 2) +
  labs(
    title = "Qst Values Across Replications for Each Sample Size",
    x = "Sample Size",
    y = "Qst Value"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

```

Second qqplot of sample 
```{r}
library(gridExtra)
library(ggplot2)

# Initialize a list to store QQ plot data for each replication
qqplot_data_list <- list()

# Define pairs of sample sizes for QQ plots
sample_pairs <- list(
  c("sample_1", "sample_10"),
  c("sample_1", "sample_100"),
  c("sample_1", "sample_1000"),
  c("sample_10", "sample_100"),
  c("sample_10", "sample_1000"),
  c("sample_100", "sample_1000")
)

# Loop through each replication
for (replication_name in names(qst_sample_results$sample_1)) {
  # Initialize a list to store QQ plot data for this replication
  replication_qq_data <- list()
  
  # Loop through each pair of sample sizes
  for (pair in sample_pairs) {
    sample_1 <- pair[1]
    sample_2 <- pair[2]
    
    # Extract Qst values for the two sample sizes
    qst_1 <- qst_sample_results[[sample_1]][[replication_name]]
    qst_2 <- qst_sample_results[[sample_2]][[replication_name]]
    
    # Ensure data is aligned by replicate
    qst_1_values <- unlist(qst_1)
    qst_2_values <- unlist(qst_2)
    
    # Create a data frame for QQ plotting
    qq_data <- data.frame(
      Qst_1 = qst_1_values,
      Qst_2 = qst_2_values
    )
    
    # Create QQ plot
    qq_plot <- ggplot(qq_data, aes(sample = Qst_1, theoretical = Qst_2)) +
      stat_qq() +
      stat_qq_line() +
      labs(
        title = paste("QQ Plot:", sample_1, "vs", sample_2, "in", replication_name),
        x = paste("Theoretical Quantiles (", sample_1, ")", sep = ""),
        y = paste("Sample Quantiles (", sample_2, ")", sep = "")
      ) +
      theme_minimal()
    
    # Print each QQ plot individually
    print(qq_plot)
  }
}

```